---
title: "AS EEG analysis"
author: "Abby Beatty"
date: "2026-05-08"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

general figure theme:
axis line size = .3
axis title size = 6
axis text size = 5
line size = .4 or .5
alpha ribbon = 0.3
alpha points = 0.25
alpha line for lunaid = 0.25
marker = 16
marker size = 0.5


## Functions
```{r functions}
# convert power in uV^2 to dB
uV2_to_dB <- function(uV2){
  dB <- 10*log10(uV2)
}

# outlier detection of lmer models
outlier_modelresiduals <- function(df, model_residuals, var2clean){
  # z-score residuals
  residuals_z <- scale(model_residuals)[,1]
  # new column name
  newcolname <- paste0(var2clean,"_clean")
  # outlier variables to NA
  df <- df %>%
    mutate(
      !!newcolname := if_else(
        abs(residuals_z)>2 | is.na(residuals_z),
        NA,
        .data[[var2clean]])
    )
  # remove outlier rows
  df <- df %>% filter(!is.na(!!sym(newcolname)))
  return(df)
}

# plot points removed from outlier detection
plot_removedpoints <- function(cleaned_df, 
                               xvar, yvar, groupvar, 
                               cleanedvar,
                               xlab_title, ylab_title, 
                               plot_title, plot_subtitle,
                               label1, label2){
  # data frame of removed points
  removed_points <- cleaned_df %>%
    filter(is.na({{ cleanedvar }}))
  # plot
  q <- ggplot(data = cleaned_df) + 
    geom_point(aes(x={{ xvar }}, # plot original points
                   y={{ yvar }}),
               color='black',
               alpha=0.5)+
    geom_line(aes(x = {{xvar}}, 
                  y={{ yvar }}, 
                  group = {{ groupvar }}),
              color='black',
              alpha=0.5)+
    geom_point(data = removed_points, # plot removed points
               aes(x = {{xvar}},
                   y = {{yvar}}),
               color='red')+
    geom_line(data = removed_points,
              aes(x={{xvar}},
                  y={{yvar}},
                  group={{groupvar}}),
              color='red',
              alpha=0.5)+
    geom_text_repel(data = removed_points, # plot labels of removed data
                  aes(x = {{xvar}},
                      y = {{yvar}},
                      label = paste0({{label1}},"_",{{label2}})),
                  size = 3, 
                  color = "red") +
    xlab({{xlab_title}}) + ylab({{ ylab_title}})+
    ggtitle({{plot_title}})+
    labs(subtitle = {{plot_subtitle}}) +
    theme(
          plot.title = element_text(size = 11, face='plain', hjust=0),
          plot.subtitle = element_text(size=10, face='plain',hjust=0),
          axis.title = element_text(size=8),
          panel.background = element_rect(fill='white'),
          axis.line = element_line(color='black'),
          legend.text = element_text(size=8),
          legend.title = element_text(size = 8),
          axis.text = element_text(size=8)
        )
  print(q)
    
}

# extract ROI name from column name
roi_from_name <- function(x) {
  str_extract(x,"(?<=sipfc\\.)[^_]+")
}

# extract Metabolite from column name
metabolite_from_name <- function(x) {
  str_extract(x,"(?<=_)[^_]+(?=(_|$))")
}
```

## Load libraries
```{r load libraries}
library(paletteer)
library(patchwork)
library(ggnewscale)
library(dplyr)
library(viridis)
library(gratia)
library(R.matlab)
library(ggplot2)
library(ggrepel)
library(ggdist)
library(lme4)
library(LNCDR)
library(lmerTest)
library(reshape2)
library(scales)
library(tidyr)
library(gridExtra)
library(ggpubr)
library(mgcv)
library(emmeans)
library(modelr)
library(stringr)
library(boot)
library(mediation)
library(lmeresampler)
library(ggeffects)
library(sjPlot)
library(interactions)
library(grid)
library(ggeffects)
```

## Load and merge data
```{r load and merge data}
# load data from cluster power/ersp table
clusterpower_df <- read.csv('/Volumes/Hera/Abby/AS_EEG/Results/ersp_itc_clusters_avgtrl_20260508.csv')
clusters_df <- read.csv('/Volumes/Hera/Abby/AS_EEG/Results/ersp_itc_clusterinfo_avgtrl_20260508.csv')

broadband_df <- read.csv('/Volumes/Hera/Abby/AS_EEG/Results/broadband_sponevo_20260508.csv')

# merge broadband and ersp data frames
sponevo_ersp_df <- merge(clusterpower_df,broadband_df, by = c("lunaid","eeg_date","eeg_age","sex","PercentErrCor","Accuracy","AvgLatCor",
                                                             "CVLatCor","AvgLatErrCor","CVLatErrCor","NumCor","NumErrCor","NumIncor",
                                                             "NumDrop","Total","Viable"))

# make lunaid a factor
sponevo_ersp_df$lunaid <- as.factor(sponevo_ersp_df$lunaid)

# add visit number
sponevo_ersp_df <- sponevo_ersp_df %>%
  group_by(lunaid) %>%
  mutate(visit = row_number()) %>%
  ungroup()

# calculate correct response rate
sponevo_ersp_df$CorRate <- sponevo_ersp_df$NumCor / (sponevo_ersp_df$NumCor + sponevo_ersp_df$NumErrCor)

# columns to no convert to dB
cols_no_convert <- c("lunaid","eeg_date","eeg_age","sex",
                     "PercentErrCor","AvgLatCor","CVLatCor",
                     "AvgLatErrCor","CVLatErrCor","NumCor",
                     "NumErrCor","NumDrop","NumIncor","Total",
                     "Viable","visit","CorRate","Accuracy","CorRate")

# columns to convert to dB
cols_to_convert <- sponevo_ersp_df %>%
  dplyr::select(contains("power"), -all_of(cols_no_convert)) %>%
  names()

# convert power values from uV^2 to dB
sponevo_ersp_df_dB <- sponevo_ersp_df %>%
  mutate(
    across(
      .cols = all_of(cols_to_convert),
      .fns = ~ uV2_to_dB(.x),
      .names = "{.col}_dB"
    )
  )

# make sure dB matrix lunaid is factor
sponevo_ersp_df_dB$lunaid <- factor(sponevo_ersp_df_dB$lunaid, levels = levels(sponevo_ersp_df_dB$lunaid))

# load merged7t for glutamate values
merged7t <- read.csv('/Volumes/Hera/Projects/7TBrainMech/scripts/txt/merged_7t.csv')
merged7t_glugaba <- merged7t %>% dplyr::select(lunaid,sess.age,
                                        visitno,sex ,top.mri.date,
                                        matches("DLPFC.*GluGaba_Asym"),
                                        matches("DLPFC.*Glu_gamadj"),
                                        matches("DLPFC.*GABA_gamadj"),
                                        matches("DLPFC.*Glu_SD"),
                                        matches("DLPFC.*GABA_SD"))

# make lunaid a factor
merged7t_glugaba$lunaid <- as.factor(merged7t_glugaba$lunaid)

# transform glu/gaba asymmetry by taking the square root: do not want to transform gamadj or ratio
gamadj_cols <- colnames(merged7t_glugaba %>% dplyr::select(ends_with("gamadj") 
                                                    | ends_with("Ratio")
                                                    | ends_with("SD")))

cols_no_trans <- c("lunaid","sess.age","top.mri.date","visitno",gamadj_cols)
cols_to_trans <- merged7t_glugaba %>%
  dplyr::select(where(is.numeric), -all_of(cols_no_trans)) %>%
  names()
merged7t_glugaba <- merged7t_glugaba %>%
  mutate(
    across(
      .cols = all_of(cols_to_trans),
      .fns = ~ sqrt(.x),
      .names = "{.col}_sqrt"
    )
  )

# get names of ROIs
not_trans <- merged7t_glugaba %>%
  dplyr::select(ends_with("_Asym") | ends_with("_SD")) %>%
  names()
# names %>% grepl
not_roi_names <- c(not_trans, "lunaid","sess.age","visitno","sex","top.mri.date")

names_rois <- merged7t_glugaba %>%
  dplyr::select(-all_of(not_roi_names)) %>%
  names()
 # ^^ don't want to look at untransformed asymmetry values

# join mrsi data and eeg data
main_df <- merge(merged7t_glugaba, sponevo_ersp_df_dB,
                 by.x = c("lunaid","visitno"),
                 by.y = c("lunaid","visit"),
                 all.x=T)

# make sure lunaid is a factor
main_df$lunaid <- factor(main_df$lunaid, levels = 
                             levels(merged7t_glugaba$lunaid))

# calculate difference in sess.age and eeg_age and take absolute value
main_df <- main_df %>%
  mutate(diffage = abs(sess.age - eeg_age))

# Make sex a categorical variable
main_df$sex <- as.factor(main_df$sex.x)

# Filter out non-viable subs
main_df_viable <- main_df %>% filter(Viable==1)
main_df_viable$invage <- 1/main_df_viable$eeg_age
main_df_viable$diff_broadband_spon <- main_df_viable$corAS_broadband_sponpower_dB -
  main_df_viable$VGS_broadband_sponpower_dB
main_df_viable$diff_broadband_evo <- main_df_viable$corAS_broadband_evopower_dB -
  main_df_viable$VGS_broadband_evopower_dB
main_df_viable <- main_df_viable %>% mutate(
  age_cat = ifelse(
    eeg_age < 17,"kid",
    ifelse(
      eeg_age>=23,
      "adult",
      'adolescent'
    )
  )
)
main_df_viable$age_cat <- factor(main_df_viable$age_cat, 
                                 levels = c("kid","adolescent","adult"))
```

## Description of data
```{r descriptive stats}
hist(main_df$eeg_age)

main_df <- main_df %>%
  mutate(
    eeg_age_viable = ifelse(Viable==1,
                            eeg_age,
                            NA)
  )
hist(main_df$eeg_age_viable)

# is the mean age significantly different after removing non-viable subjects
t.test(main_df$eeg_age, main_df$eeg_age_viable)
main_df_long <- pivot_longer(main_df, cols = c("eeg_age","eeg_age_viable"),
                             # names_to = "agetype",
                             # values_to = "age"
                             )
main_df_long$name <- as.factor(main_df_long$name)
lmermodel <- lmerTest::lmer(value ~ name + (1|lunaid),
                            data=main_df_long)
summary(lmermodel)

cat(
  # Total number of unique subjects
  "Total subjects: ", length(unique(main_df$lunaid)),
  " (", length(unique(main_df$lunaid[main_df$sex.x == "F"])), " F)", "\n",
  range(main_df$eeg_age, na.rm = TRUE)[1], "-",
  range(main_df$eeg_age, na.rm = TRUE)[2], " years old\n\n",
  
  # Total number of unique subjects that have AS EEGs
  "Total AS EEG subjects: ", main_df %>% filter(!is.na(Total)) %>% pull(lunaid) %>% n_distinct(),
  " (", main_df %>% filter(!is.na(Total), sex.x=="F") %>% pull(lunaid) %>% n_distinct(), " F)", "\n",
  main_df %>%
  filter(!is.na(Total)) %>% pull(eeg_age) %>% range() %>% .[1], "-",
  main_df %>%
  filter(!is.na(Total)) %>% pull(eeg_age) %>% range() %>% .[2], " years old\n\n",
  
  # Total number of AS main_df
  "Total AS EEGs: ", main_df %>% filter(!is.na(Total)) %>% nrow(),"\n\n",
  
  # Total number of viable AS EEG 
  "Total viable AS EEGs: ", main_df %>% filter(!is.na(Total),Viable==1) %>% nrow(),
  "\n\nTotal viable AS EEG subjects: ", main_df %>% 
    filter(!is.na(Total),Viable==1) %>% pull(lunaid) %>% n_distinct(),
  " (", main_df %>% filter(!is.na(Total), Viable==1, sex.x=="F") %>% pull(lunaid) %>% n_distinct()," F)\n",
   main_df %>%
  filter(!is.na(Total),Viable==1) %>% pull(eeg_age) %>% range() %>% .[1],"-",
   main_df %>%
  filter(!is.na(Total),Viable==1) %>% pull(eeg_age) %>% range() %>% .[2], " years old\n\n",
  
  # Total number of unqiue subject's with DLPFC Glu/GABA asymmetry value
  "Total DLPFC Glu-GABA Asym MRSI subjects: ", main_df %>%
    filter(!is.na(sipfc.DLPFC_GluGaba_Asym_sqrt)) %>% pull(lunaid) %>% n_distinct(),
  " (", main_df %>% 
    filter(!is.na(sipfc.DLPFC_GluGaba_Asym_sqrt), sex.x=="F") %>% pull(lunaid) %>% n_distinct(), " F)", "\n",
  main_df %>%
  filter(!is.na(sipfc.DLPFC_GluGaba_Asym_sqrt)) %>% pull(sess.age) %>% range() %>% .[1], "-",
  main_df %>%
  filter(!is.na(sipfc.DLPFC_GluGaba_Asym_sqrt)) %>% pull(sess.age) %>% range() %>% .[2],
  " years old\n\n",
  
  # Total number of DLPFC scans
  "Total DLPFC Glu-GABA Asym MRSI scans: ", main_df %>%
    filter(!is.na(sipfc.DLPFC_GluGaba_Asym_sqrt)) %>% nrow(),
  " (", main_df %>%
    filter(!is.na(sipfc.DLPFC_GluGaba_Asym_sqrt), sex.x =="F") %>% nrow(), " F)","\n", 
  
  # Totals of subjects with both viable AS eegs and DLPFC mrsi data
   "Total DLPFC Glu-GABA Asym MRSI and viable AS EEG subjects: ", main_df %>%
    filter(!is.na(sipfc.DLPFC_GluGaba_Asym_sqrt), !is.na(Total), Viable==1) %>% pull(lunaid) 
  %>% n_distinct(),
  " (", main_df %>% 
    filter(!is.na(sipfc.DLPFC_GluGaba_Asym_sqrt), !is.na(Total), Viable==1, sex.x=="F") %>% 
    pull(lunaid) %>% n_distinct(), " F)", "\n",
  main_df %>%
  filter(!is.na(sipfc.DLPFC_GluGaba_Asym_sqrt), !is.na(Total), Viable==1) %>%
    pull(sess.age) %>% range() %>% .[1], "-",
  main_df %>%
  filter(!is.na(sipfc.DLPFC_GluGaba_Asym_sqrt), !is.na(Total), Viable==1) %>% pull(sess.age) 
  %>% range() %>% .[2],
  " years old\n\n",
  "Total DLPFC Glu-GABA Asym MRSI and viable AS EEGs: ", main_df %>%
    filter(!is.na(sipfc.DLPFC_GluGaba_Asym_sqrt), !is.na(Total), Viable==1) %>% nrow(),"\n\n",
  sep=""
)

# Waterfall plot
d <- data.frame(age = main_df$eeg_age, id=main_df$lunaid, Sex = as.factor(main_df$sex.x))
p <- waterfall_plot(d,color=Sex)
p + scale_color_manual(name = "",values = c("red4","blue4"),labels = c("Female","Male"))+
  ggtitle("7T EEG")


d <- data.frame(age = main_df$eeg_age_viable, 
                id=main_df$lunaid, Sex = as.factor(main_df$sex.x))
p <- waterfall_plot(d,color=Sex)
p + scale_color_manual(name = "",values = c("red4","blue4"),labels = c("Female","Male")) +
  ggtitle("7T Viable AS EEG")

```

## Behavior age effects
```{r}

run_behavior_analysis <- function(b, df, behav_titles, behav_labels, behavs){
  # define temp data frame
  temp_df <- data.frame(
    lunaid = df$lunaid,
    eeg_date = df$eeg_date,
    sex = df$sex,
    eeg_age = df$eeg_age,
    invage = df$invage,
    behav = df[[b]],
    visit = df$visitno
  )
  
  # run linear model w/o random effects
  lm_model <- lm(behav ~ invage + sex, data = temp_df, na.action = na.exclude)
  df_clean <- outlier_modelresiduals(temp_df,residuals(lm_model),"lunaid")
  df_clean$lunaid_clean <- as.factor(df_clean$lunaid_clean)
  
  # run with cleaned data and random effects
  lmer_model <- lmerTest::lmer(behav ~ invage + sex + (1|lunaid_clean),
                               data = df_clean,
                               na.action = na.exclude)
  print(b)
  print(summary(lmer_model))
  
  # build lmer plot
  temp_plot_df <- df_clean %>% filter(!is.na(lunaid_clean))
  b_index <- match(b,behavs)
  
  behavage_fig <- ggplot(temp_plot_df, aes(x=eeg_age, y=behav)) + 
    geom_point(alpha = 0.25, shape = 16, size = 0.5) +
    geom_line(alpha = 0.25, aes(group = lunaid_clean), linewidth = 0.2) +
    geom_smooth(method = "lm", formula = y ~ I(1/x), color = "black",
                alpha = 0.5, linewidth = 0.5) +
    xlab("Age (years)") + ylab(behav_labels[b_index]) +
    ggtitle(behav_titles[b_index]) +
    theme(
      plot.title = element_text(size = 5, face = 'bold', hjust = 0),
      axis.title = element_text(size = 5),
      panel.background = element_rect(fill = 'white'),
      axis.line = element_line(color = 'black',size=0.3),
      axis.text = element_text(size = 4)
    )
  # print(behavage_fig)
  
  # save summary
  lmer_summary <- summary(lmer_model)
  results <- data.frame(behav = b, 
                           EF = lmer_summary$coefficients["invage","Estimate"],
                           t =  lmer_summary$coefficients["invage","t value"],
                           p = lmer_summary$coefficients["invage","Pr(>|t|)"]
                           )
  # run GAM
  gam_model <- gam(behav ~ s(eeg_age, k = 3) + sex, data = temp_df, na.action = na.exclude)
  df_clean <- outlier_modelresiduals(temp_df, residuals(gam_model), "lunaid")
  df_clean$lunaid_clean <- as.factor(df_clean$lunaid_clean)
  
  gamre_model <- gam(behav ~ s(eeg_age, k = 3) + sex + s(lunaid_clean, bs = 're'),
                     data = df_clean, na.action = na.exclude)
  print(summary(gamre_model))
  derivs <- derivatives(gamre_model, select = "s(eeg_age)", type = "central",
                        interval = "simultaneous",n=200)
  derivs$significant <- !(derivs$.lower_ci <= 0 & derivs$.upper_ci >= 0)
  # print(draw(derivs) +
  #         geom_ribbon(aes(ymin = .lower_ci, ymax = .upper_ci,
  #                         fill = significant), alpha = 0.3))
  # ages where derivative is significant
  sig_ages <- derivs$eeg_age[derivs$significant]
  print(paste("Derivative is significant from age", min(sig_ages), "to age", max(sig_ages)))
  
  temp_plot_df <- df_clean %>% filter(!is.na(lunaid_clean))
  behavage_fig_gam <- ggplot(temp_plot_df, aes(x = eeg_age, y = behav)) +
    geom_point(alpha = 0.25, shape = 16, size = 0.5) +
    geom_line(alpha = 0.25, aes(group = lunaid_clean),linewidth = 0.2) +
    geom_smooth(method = "gam", formula = y ~ s(x, k = 3), color = "black", 
                alpha = 0.5, linewidth = 0.5) +
    xlab("Age (years)") + ylab(behav_labels[b_index]) +
    ggtitle(behav_titles[b_index]) +
    theme(
      plot.title = element_text(size = 5, face = 'bold', hjust = 0),
      axis.title = element_text(size = 5),
      panel.background = element_rect(fill = 'white'),
      axis.line = element_line(color = 'black',size=0.3),
      axis.text = element_text(size = 4)
    )
  # print(behavage_fig_gam)
  
  # return plots and results
  list(plot_lmer = behavage_fig, plot_gam = behavage_fig_gam, result_row = results)
}

# defining behavior variables
behavs <- c("CorRate","CVLatCor","AvgLatCor")
# plot settings
behav_titles <- c("Correct Response Rate","Latency Variability","Average Latency")
behav_labels <- c('% correct','Coefficient of variation','Latency (ms)')

results <- lapply(behavs, run_behavior_analysis,
                  df = main_df_viable,
                  behav_titles = behav_titles,
                  behav_labels = behav_labels,
                  behavs = behavs)
P_behav <- setNames(lapply(results, '[[', "plot_lmer"),behavs)
P_behav_gam <- setNames(lapply(results,'[[',"plot_gam"),behavs)
R_behav <- do.call(rbind, lapply(results, '[[',"result_row"))
```

## Broadband spontaneous and evoked power
### Age effects
```{r}
run_power_interaction <- function(col_AS, col_VGS, color_AS,
                                  df, powertype) {
  # ---- Pivot data and run lmer ----
  df_long <- pivot_longer(df, cols = c(col_AS, col_VGS),
                          names_to = "condition",
                          values_to = "power")
  df_long$condition <- as.factor(df_long$condition)
  
  # ---- Linear model w/o random effects ----
  lm_model <- lm(power ~ invage*condition + sex, data = df_long,
                 na.action = na.exclude)
  df_clean <- outlier_modelresiduals(df_long, residuals(lm_model),"lunaid")
  df_clean$lunaid_clean <- as.factor(df_clean$lunaid_clean)
  
  # ---- Linear model with random effects ----
  lmer_model <- lmerTest::lmer(power ~ invage*condition + sex + (1|lunaid_clean),
                               data=df_clean,
                               na.action = na.exclude)
  lmer_summary <- summary(lmer_model)
  print(lmer_summary)
  results_lmer <- data.frame(powertype = powertype, 
                             p_interaction = lmer_summary$coefficients[5,5],
                             p_age = lmer_summary$coefficients[2,5],
                             p_condition = lmer_summary$coefficients[3,5]) 
  
  # build lmer plot
  plot_df <- df_clean %>% filter(!is.na(lunaid_clean))
  # marginal means
  emm_lmer <- emmeans(lmer_model, ~ condition | invage ,
                      at = list(invage = seq(min(df_clean$invage,na.rm=T),
                                             max(df_clean$invage,na.rm=T),
                                             length.out = 100)))
  emm_df_lmer <- as.data.frame(emm_lmer)
  emm_df_lmer$age <- 1/emm_df_lmer$invage
  
  # ---- LMER Age trajectory w/ points ----
  fig_wpts <- ggplot() +
    geom_point(data = plot_df, aes(x = eeg_age, y = power, color = condition),
               alpha = 0.3, size = 0.5, shape = 16) +
    geom_line(data = plot_df, aes(x = eeg_age, y = power, color = condition,
                                  group = interaction(lunaid_clean, condition)),
              alpha = 0.25, size = 0.2) +
    geom_line(data = emm_df_lmer, aes(x = age, y = emmean, color = condition),
                linewidth = 0.4) +
    scale_color_manual(name = "Condition",
                       values = c(setNames(color_AS, col_AS), "grey30" |> setNames(col_VGS)),
                       labels = c(setNames("AS", col_AS), setNames("VGS", col_VGS))) +
    xlab("Age (years)") + ylab("Power (dB)") + theme_classic() +
    theme(axis.title = element_text(size = 6), axis.text = element_text(size = 5),
          axis.line = element_line(size = 0.3), axis.ticks = element_line(size = 0.3),
          legend.text = element_text(size = 4), legend.title = element_text(size = 5))
  # print(fig_wpts)
  
  # ---- Johnson-Neyman ----
  df_clean$cond_num <- ifelse(df_clean$condition == col_AS, 1, 0)
  lmer_jn <- lmerTest::lmer(power ~ invage * cond_num + sex + (1|lunaid_clean),
                            data = df_clean, na.action = na.exclude)
  print(summary(lmer_jn))
  jn <- johnson_neyman(model = lmer_jn, pred = "cond_num", modx = "invage")
  lmer_agebounds <- 1 / jn$bounds
  print(lmer_agebounds)
  
  # ---- Difference plot with significant ages highlighted ----
  invage_grid <- seq(min(df_clean$invage, na.rm=T),
                     max(df_clean$invage, na.rm=T),
                     length.out = 100)
  emm_age <- emmeans(lmer_model, ~ condition | invage, at = list(invage = invage_grid))
  contrast_df <- contrast(emm_age, method = 'pairwise') %>% confint() %>% as.data.frame()
  if (powertype == "spontaneous"){
    contrast_df <- contrast_df %>%
      mutate(age = 1/invage, 
             diff = estimate,
             conf.low = lower.CL, 
             conf.high = upper.CL) %>%
      arrange(age) %>%
      mutate(sig.age      = ifelse(age <= lmer_agebounds[2] | age >= lmer_agebounds[1], 1, 0),
             y_sig        = ifelse(sig.age == 1, diff, NA),
             conf.high_sig = ifelse(sig.age == 1, conf.high, NA),
             conf.low_sig  = ifelse(sig.age == 1, conf.low, NA))
  }
  
  if (powertype == "evoked"){
    contrast_df <- contrast_df %>%
      mutate(age = 1/invage, 
             diff = estimate,
             conf.low = lower.CL, 
             conf.high = upper.CL) %>%
      arrange(age) %>%
      mutate(sig.age      = ifelse(age >= lmer_agebounds[2] | age <= lmer_agebounds[1], 0, 1),
             y_sig        = ifelse(sig.age == 1, diff, NA),
             conf.high_sig = ifelse(sig.age == 1, conf.high, NA),
             conf.low_sig  = ifelse(sig.age == 1, conf.low, NA))
  }
  # ---- Plot difference LMER ----
  diff_split_fig <- ggplot(data = contrast_df, aes(x = age)) +
    geom_hline(yintercept = 0, linetype = 'dashed', color = 'black', size = 0.2) +
    geom_line(aes(y = diff), color = 'grey30', size = 0.2, alpha = 0.5) +
    geom_line(aes(y = y_sig), color = color_AS, size = 0.5) +
    geom_ribbon(aes(ymin = conf.low, ymax = conf.high), fill = "grey30", alpha = 0.1,
                color = NA) +
    geom_ribbon(aes(ymax = conf.high_sig, ymin = conf.low_sig), fill = color_AS, alpha = 0.3,
                color = NA) +
    xlab("Age (yrs)") + ylab("AS - VGS power (dB)") + theme_classic() +
    theme(axis.title = element_text(size = 5), axis.text = element_text(size = 3),
          axis.line = element_line(linewidth = 0.2), 
          axis.ticks = element_line(linewidth = 0.2),
          plot.margin = margin(0,0,0,0,unit="mm"))
  # print(diff_split_fig)
  
  # --- plot sex differences lmer ---
  emm_sex <- emmeans(lmer_model, ~ sex | invage,
                     at = list(invage = seq(min(df_clean$invage,na.rm=T),
                                             max(df_clean$invage,na.rm=T),
                                             length.out=100)))
  emm_sex_df <- as.data.frame(emm_sex)
  emm_sex_df$eeg_age <- 1/emm_sex_df$invage
  fig_sex <- ggplot() +
  geom_point(data = df_clean, aes(x = eeg_age, y = power, color = sex),
             alpha = 0.3, size = 0.5, shape = 16) +
  geom_line(data = df_clean, aes(x = eeg_age, y = power, color = sex,
                                  group = interaction(lunaid_clean, sex)),
            alpha = 0.25, size = 0.2) +
  geom_line(data = emm_sex_df, aes(x = eeg_age, y = emmean, color = sex),
            linewidth = 0.4) +
    scale_color_manual(name = "Sex",
                       values = c("M"="#C9B82A",
                                  "F" = "#62B03C"))+
  xlab("Age (years)") + ylab("Power (dB)") + theme_classic() +
  theme(axis.title = element_text(size = 6), axis.text = element_text(size = 5),
        axis.line = element_line(size = 0.3), axis.ticks = element_line(size = 0.3),
        legend.text = element_text(size = 4), legend.title = element_text(size = 5))
  
  # ---- GAM w/o random effects ----
  gam_model <- gam(power ~ s(eeg_age,by = condition,k=3) + condition + sex, data = df_long,
                   na.action = na.exclude, method='REML')
  df_clean <- outlier_modelresiduals(df_long, residuals(gam_model),"lunaid")
  df_clean$lunaid_clean <- as.factor(df_clean$lunaid_clean)
  gamre_model <- gam(power ~ s(eeg_age,by=condition,k=3) + condition + sex + s(lunaid_clean,bs='re'),
                     data=df_clean,
                     na.action = na.exclude)
  print(summary(gamre_model))
  
  plot_df <- df_clean %>% filter(!is.na(lunaid_clean))
  emm_gam <- emmeans(gamre_model, ~ condition | eeg_age,
                        at = list(eeg_age = seq(min(df_clean$eeg_age,na.rm=T),
                                                max(df_clean$eeg_age,na.rm=T),
                                                length.out=100)))
  emm_df_gam <- as.data.frame(emm_gam)

  fig_wpts_gam <-  ggplot() +
  geom_point(data = df_clean, aes(x = eeg_age, y = power, color = condition),
             alpha = 0.3, size = 0.5, shape = 16) +
  geom_line(data = df_clean, aes(x = eeg_age, y = power, color = condition,
                                group = interaction(lunaid_clean, condition)),
            alpha = 0.25, size = 0.2) +
  geom_line(data = emm_df_gam, aes(x = eeg_age, y = emmean, color = condition),
              method = "gam",linewidth = 0.4) +
  scale_color_manual(name = "Condition",
                     values = c(setNames(color_AS, col_AS), setNames("grey30", col_VGS)),
                     labels = c(setNames("AS", col_AS), setNames("VGS", col_VGS))) +
  xlab("Age (years)") + ylab("Power (dB)") + theme_classic() +
  theme(axis.title = element_text(size = 6), axis.text = element_text(size = 5),
        axis.line = element_line(size = 0.3), axis.ticks = element_line(size = 0.3),
        legend.text = element_text(size = 4), legend.title = element_text(size = 5))
  # print(fig_wpts_gam)
  
  # ---- Is the difference in gam plots significant? ----
  # compare to null model
  gamre_null <- gam(power ~ s(eeg_age,k=3) + condition + sex + s(lunaid_clean,bs='re'),
                    data= df_clean, na.action = na.exclude)
  aic_gam <- AIC(gamre_null, gamre_model)
  anova_gam <- anova(gamre_null, gamre_model, test = "Chisq")
  print(aic_gam)
  print(anova_gam)
  
  # ---- Plot difference plot GAM ----
  age_grid <- seq(min(df_clean$eeg_age, na.rm=T), 
                  max(df_clean$eeg_age, na.rm=T),
                  length.out = 100)
  
  emm_gam <- emmeans(gamre_model, ~ condition | eeg_age, 
                     at = list(eeg_age = age_grid))
  contrast_df_gam <- contrast(emm_gam, method = 'pairwise') %>% 
    confint() %>% 
    as.data.frame()
  
  if (powertype == "spontaneous"){
   contrast_df_gam <- contrast_df_gam %>%
    mutate(
      diff      =  estimate,
      conf.low  =  lower.CL,
      conf.high =  upper.CL,
      sig       = ifelse(conf.low > 0 | conf.high < 0, 1,0),
      y_sig     = ifelse(sig == 1, diff, NA),
      ci_hi_sig = ifelse(sig == 1, conf.high, NA),
      ci_lo_sig = ifelse(sig == 1, conf.low, NA)
      )
  }
  
  
  if (powertype == "evoked"){
    contrast_df_gam <- contrast_df_gam %>%
    mutate(
      diff      =  estimate,
      conf.low  =  lower.CL,
      conf.high =  upper.CL,
      sig       = ifelse(conf.low > 0 | conf.high < 0, 0,1),
      y_sig     = ifelse(sig == 1, diff, NA),
      ci_hi_sig = ifelse(sig == 1, conf.high, NA),
      ci_lo_sig = ifelse(sig == 1, conf.low, NA)
      )
  }
  # see which ages are significant
  gam_agebounds <- contrast_df_gam %>% 
    filter(sig == 0) %>% 
    summarise(min_age = min(eeg_age), max_age = max(eeg_age))
  
  gam_diff_split <- ggplot(data = contrast_df_gam, aes(x = eeg_age)) +
    geom_hline(yintercept = 0, linetype = 'dashed', color = 'black', size = 0.2) +
    geom_line(aes(y = diff), color = 'grey30', size = 0.2, alpha = 0.5) +
    geom_line(aes(y = y_sig), color = color_AS, size = 0.5) +
    geom_ribbon(aes(ymin = conf.low, ymax = conf.high), 
                fill = "grey30", alpha = 0.1, color = NA) +
    geom_ribbon(aes(ymin = ci_lo_sig, ymax = ci_hi_sig), 
                fill = color_AS, alpha = 0.3, color = NA) +
    xlab("Age (yrs)") + ylab("AS - VGS power (dB)") + theme_classic() +
    theme(axis.title = element_text(size = 5), axis.text = element_text(size = 3),
          axis.line = element_line(linewidth = 0.2), axis.ticks = element_line(linewidth = 0.2),
          plot.margin = margin(0,0,0,0,unit="mm"))
  # print(gam_diff_split)
  
  # --- plot sex differences GAM ---
  emm_sex_gam <- emmeans(gamre_model, ~ sex | eeg_age,
                     at = list(eeg_age = seq(min(df_clean$eeg_age,na.rm=T),
                                             max(df_clean$eeg_age,na.rm=T),
                                             length.out=100)))
  emm_sex_df_gam <- as.data.frame(emm_sex_gam)
  fig_sex_gam <- ggplot() +
  geom_point(data = df_clean, aes(x = eeg_age, y = power, color = sex),
             alpha = 0.3, size = 0.5, shape = 16) +
  geom_line(data = df_clean, aes(x = eeg_age, y = power, color = sex,
                                  group = interaction(lunaid_clean, sex)),
            alpha = 0.25, size = 0.2) +
  geom_line(data = emm_sex_df_gam, aes(x = eeg_age, y = emmean, color = sex),
            linewidth = 0.4) +
    scale_color_manual(name = "Sex",
                       values = c("M"="#C9B82A",
                                  "F" = "#62B03C"))+
  xlab("Age (years)") + ylab("Power (dB)") + theme_classic() +
  theme(axis.title = element_text(size = 6), axis.text = element_text(size = 5),
        axis.line = element_line(size = 0.3), axis.ticks = element_line(size = 0.3),
        legend.text = element_text(size = 4), legend.title = element_text(size = 5))
  
  # ----- Return all plots and results ----
  list(trajplot_lmer = fig_wpts, trajplot_gam = fig_wpts_gam, 
              diffplot_lmer = diff_split_fig, diffplot_gam = gam_diff_split,
              results_row_lmer = results_lmer, aic_gam = aic_gam, anova_gam = anova_gam,
       ages_lmer = lmer_agebounds, ages_gam = gam_agebounds, fig_sex_lmer = fig_sex,
       fig_sex_gam = fig_sex_gam)
}

results_spontaneousage <- run_power_interaction(col_AS = "corAS_broadband_sponpower_dB",
                                             col_VGS = "VGS_broadband_sponpower_dB",
                                             color_AS = '#67428F',df = main_df_viable,
                                             powertype = "spontaneous")
P_spontraj <- results_spontaneousage$trajplot_lmer
# P_spontraj
P_spontraj_gam <- results_spontaneousage$trajplot_gam
P_spondiff <- results_spontaneousage$diffplot_lmer
P_spondiff_gam<- results_spontaneousage$diffplot_gam
# P_spondiff
P_sponsex <- results_spontaneousage$fig_sex_lmer
P_sponsex
P_sponsex_gam <- results_spontaneousage$fig_sex_gam
P_sponsex_gam

results_evokedage <- run_power_interaction(col_AS = "corAS_broadband_evopower_dB",
                                             col_VGS = "VGS_broadband_evopower_dB",
                                             color_AS = '#388599',df = main_df_viable,
                                             powertype = "evoked")
P_evotraj <- results_evokedage$trajplot_lmer
# P_evotraj
P_evodiff <- results_evokedage$diffplot_lmer
# P_evodiff
P_evotraj_gam <- results_evokedage$trajplot_gam
# P_evotraj
P_evodiff_gam <- results_evokedage$diffplot_gam
# P_evodiff
P_evosex <- results_evokedage$fig_sex_lmer
P_evosex
P_evosex_gam <- results_evokedage$fig_sex_gam
P_evosex_gam

```

### Behavioral effects
#### Main effects
```{r}
### Associations with behavior
#### Main effects
powertypes <- c("spon","evo")
R_BroadbandAge <- data.frame()
R_BroadbandBehav <- data.frame()
R_BroadbandBehav_gam <- data.frame()
P_broadbandbehav <- list()
P_broadbandbehav_gam <- list()
P_broadbandage <- list()
# defining behavior variables

behavs <- c("CorRate","CVLatCor","AvgLatCor")

# plot settings
powertypes_titles <- c("Spontaneous","Evoked")

# plotting settings
behavior_title <- c("Correct Response Rate","Latency Variability","Average Latency")
behavior_yaxis <- c('% correct','Coefficient of variation','Latency (ms)')

# loop over power types
for (p in powertypes){
  # color to make plot
  COLOR <- ifelse(
    p=='spon', '#67428F',
    ifelse(
      p =='evo','#388599',
      ifelse(
        p=='tot','black'
        )
      )
    )

  # loop over behaviors
  for (b in behavs){
    # define current behavior
    currbehav_title <- behavior_title[match(b,behavs)]
    currbehav_yaxis <- behavior_yaxis[match(b,behavs)]
    
    # define temporary data frame
    temp_df_viable <- data.frame(
      lunaid = main_df_viable$lunaid,
      eeg_date = main_df_viable$eeg_date,
      eeg_age = main_df_viable$eeg_age,
      sex = main_df_viable$sex,
      invage = 1/ main_df_viable$eeg_age,
      viable = main_df_viable$Viable,
      behav = main_df_viable[[b]],
      power = 
        main_df_viable[[paste0("corAS_broadband_",p,"power_dB")]]
         # main_df[[paste0("VGS_",p,"power_dB")]]
      )
    
    # run linear model w/o repeated measures
    lm_model <- lm(behav ~ power+ invage + sex, data = temp_df_viable,
                   na.action = na.exclude)
    # get residuals and clean
    temp_df_clean <- outlier_modelresiduals(temp_df_viable,residuals(lm_model),"lunaid")
    # make luna_id a factor
    temp_df_clean$lunaid_clean <- factor(temp_df_clean$lunaid_clean)
    
    # run with cleaned data and random effects
    lmer_model <- lmerTest::lmer(behav ~ power + invage + sex + (1|lunaid_clean), 
                                 data = temp_df_clean
                                 , na.action = na.exclude)
    new_row <- data.frame(powertype =p, behav = b, 
                          p_power = summary(lmer_model)$coefficients["power","Pr(>|t|)"])
    R_BroadbandBehav <- rbind(R_BroadbandBehav, new_row)
    # print summary
    print(paste(p,b))
    # print(summary(lmer_model))

    # plot LMER
    temp_plot_data <- temp_df_clean %>%
      filter(!is.na(lunaid_clean))

    # estimated marginal means plots
    emm_lmer <- emmeans(lmer_model, ~ power, 
                        at = list(power = seq(min(temp_df_clean$power,na.rm=T),
                                      max(temp_df_clean$power,na.rm=T),
                                      length.out=100)))
    emm_df_lmer <- as.data.frame(emm_lmer)

    q <- ggplot()+
      geom_line(data = temp_df_clean, aes(x=power,y=behav,group=lunaid),
        alpha = 0.25, size = 0.2,
        color=COLOR)+
      geom_point(data = temp_df_clean, aes(x=power,y=behav),
                  color = COLOR,
                 alpha = 0.25,shape= 16, size = 0.5)+
      geom_line(data = emm_df_lmer, aes(x=power, y=emmean),color=COLOR, linewidth = 0.5)+
      geom_ribbon(data = emm_df_lmer,
                  aes(x=power,
                      ymin=lower.CL, ymax=upper.CL)
                  ,color=NA, fill = COLOR,alpha=0.3)+
      xlab("AS Power (dB)")+
      ylab(currbehav_yaxis)+
      theme_classic()+
     theme(axis.title = element_text(size = 6),
        axis.text = element_text(size=5),
        plot.title = element_text(size = 7, face = 'bold',hjust =0),
        axis.line = element_line(size=0.3),
        axis.ticks = element_line(size=0.3),
        text = element_text(family = "sans"),
        legend.text = element_text(size = 6),
        legend.title = element_text(size = 7),
        plot.margin = margin(t = 0, r =0, l=0, b=0))
    P_broadbandbehav[[p]][[b]] <- q
    
    # print(q)
   
    ## GAM
    gam_model <- gam(behav ~ s(power,k=3) + s(eeg_age,k=3) + sex, data = temp_df_viable,
                     na.action = na.exclude)
    temp_df_clean <- outlier_modelresiduals(temp_df_viable,residuals(gam_model),"lunaid")
    gamre_model <- gam(behav ~ s(power,k=3) + s(eeg_age,k=3) + sex + s(lunaid_clean,bs='re'),
                       data = temp_df_clean, na.action = na.exclude)
    print(summary(gamre_model))
    new_row <- data.frame(powertype =p, behav = b, 
                          p_power = summary(gamre_model)$s.table["s(power)","p-value"])
    R_BroadbandBehav_gam <- rbind(R_BroadbandBehav_gam, new_row)
    # plot GAM
    temp_plot_data <- temp_df_clean %>%
      filter(!is.na(lunaid_clean))
    
    emm_gam <- emmeans(gamre_model, ~ power,
                       at = list(power = seq(min(temp_df_clean$power,na.rm=T),
                                             max(temp_df_clean$power,na.rm=T),
                                             length.out = 100)))
    emm_df_gam <- as.data.frame(emm_gam)

    q <- ggplot()+
      geom_line(data = temp_plot_data, aes(x=power,y=behav,group=lunaid),
        alpha = 0.25, size = 0.2,
        color=COLOR)+
      geom_point(data = temp_plot_data, aes(x=power,y=behav),
                  color = COLOR,
                 alpha = 0.25,shape= 16, size = 0.5)+
      geom_line(data = emm_df_gam, aes(x=power, y=emmean),color=COLOR, linewidth = 0.5)+
      geom_ribbon(data = emm_df_gam,
                  aes(x=power,
                      ymin=upper.CL, ymax=lower.CL)
                  ,color=NA, fill = COLOR,alpha=0.3)+
      xlab("AS Power (dB)")+
      ylab(currbehav_yaxis)+
      theme_classic()+
     theme(axis.title = element_text(size = 6),
        axis.text = element_text(size=5),
        plot.title = element_text(size = 7, face = 'bold',hjust =0),
        axis.line = element_line(size=0.3),
        axis.ticks = element_line(size=0.3),
        text = element_text(family = "sans"),
        legend.text = element_text(size = 6),
        legend.title = element_text(size = 7),
        plot.margin = margin(t = 0, r =0, l=0, b=0))
    P_broadbandbehav_gam[[p]][[b]] <- q

    # print(q)
  }
  
}

# adjust p-values
R_BroadbandBehav <- R_BroadbandBehav %>% 
  mutate(
    p_power_bon = p.adjust(p_power,method='bonferroni'),
    p_power_fdr = p.adjust(p_power,method='fdr')
  )
R_BroadbandBehav_gam <- R_BroadbandBehav_gam %>%
  mutate(
    p_power_bon = p.adjust(p_power,method='bonferroni'),
    p_power_fdr = p.adjust(p_power,method='fdr')
  ) 

```

#### Age interactions
```{r}
### Associations with behavior
#### Interaction effects
powertypes <- c("spon","evo")
R_BroadbandBehavInteraction <- data.frame()
P_broadbandbehavinteraction <- list()
# defining behavior variables
behavs <- c("CorRate","CVLatCor","AvgLatCor")
behavs <- c("CorRate","CVLatCor")
# plot settings
powertypes_titles <- c("Spontaneous","Evoked")

# plotting settings
behavior_title <- c("Correct Response Rate","Latency Variability","Average Latency")
behavior_yaxis <- c('% correct','Coefficient of variation','Latency (ms)')

# loop over power types
for (p in powertypes){
  # color to make plot
  COLOR <- ifelse(
    p=='spon', '#67428F',
    ifelse(
      p =='evo','#388599',
      ifelse(
        p=='tot','black'
        )
      )
    )

  # loop over behaviors
  for (b in behavs){
    # define current behavior
    currbehav_title <- behavior_title[match(b,behavs)]
    currbehav_yaxis <- behavior_yaxis[match(b,behavs)]
    
    # define temporary data frame
    temp_df_viable <- data.frame(
      lunaid = main_df_viable$lunaid,
      eeg_date = main_df_viable$eeg_date,
      eeg_age = main_df_viable$eeg_age,
      sex = main_df_viable$sex,
      invage = 1/ main_df_viable$eeg_age,
      viable = main_df_viable$Viable,
      behav = main_df_viable[[b]],
      power = 
        main_df_viable[[paste0("corAS_broadband_",p,"power_dB")]]
      )
    
    # run linear model w/o repeated measures
    lm_model <- lm(behav ~ power * invage + sex, data = temp_df_viable,
                   na.action = na.exclude)
    # get residuals and clean
    temp_df_clean <- outlier_modelresiduals(temp_df_viable,residuals(lm_model),"lunaid")
    # make luna_id a factor
    temp_df_clean$lunaid_clean <- factor(temp_df_clean$lunaid_clean)
    
    # run with cleaned data and random effects
    lmer_model <- lmerTest::lmer(behav ~ power * invage + sex + (1|lunaid_clean), 
                                 data = temp_df_clean
                                 , na.action = na.exclude)
    new_row <- data.frame(powertype =p, behav = b, 
                          p_interaction =
                            summary(lmer_model)$coefficients["power:invage","Pr(>|t|)"])
    R_BroadbandBehavInteraction <- rbind(R_BroadbandBehavInteraction, new_row)
    # print summary
    print(paste(p,b))
    print(summary(lmer_model))
    
    if(p=="spon"){
        lineVALS <- c("25" = "#231631",
                                "20" = "#67428F",
                                "14" = "#A585C7")
        pointVALS <-  c("0.04" = "#A585C7",
                                "0.05" = "#67428F",
                                "0.07" = "#231631")
      } else if (p=="evo"){
        lineVALS <-  c("25" = "#132E34",
                                "20" = "#388599",
                                "14" = "#88C4D3")
        pointVALS <- c("0.04" = "#88C4D3",
                                "0.05" = "#388599",
                                "0.07" = "#132E34")
        
      }
    
    # get JN bounds
    jn_out <- johnson_neyman(lmer_model, pred = "power",modx = "invage")
    print(1/jn_out$bounds)
    # estimated marginal means
    emm_lmer <- emmeans(lmer_model, ~ invage | power,
                        at = list(power = seq(min(temp_df_clean$power,na.rm=T),
                                  max(temp_df_clean$power,na.rm=T),
                                  length.out=100),
                                  invage = c(1/14,1/20,1/25)))
    emm_df_lmer <- as.data.frame(emm_lmer)
    emm_df_lmer$age <- factor(1/emm_df_lmer$invage, levels =  c(14,20,25))
    # predict responses
    predict_df <- predict_response(lmer_model,terms=c("power[all]","invage"))

    q <- ggplot()+
      geom_line(data = temp_df_clean, aes(x=power,y=behav,group=lunaid),
        alpha = 0.25, size = 0.2,
        color=COLOR)+
      geom_point(data = temp_df_clean, aes(x=power,y=behav),
                  color = COLOR,
                 alpha = 0.25,shape= 16, size = 0.5)+
      new_scale_fill()+
      new_scale_color()+
      geom_line(data = emm_df_lmer, aes(x=power, y=emmean,color = age),
        linewidth = 0.5)+
      geom_ribbon(data = emm_df_lmer,
                  aes(x=power,y=emmean,
                      ymin=lower.CL, ymax=upper.CL, fill = age)
                  ,color=NA,alpha=0.3)+
      scale_color_manual(name = "Age (years)", values = lineVALS) +
      scale_fill_manual(name  = "Age (years)", values = lineVALS) +
      xlab("AS Power (dB)")+
      ylab(currbehav_yaxis)+
      theme_classic()+
     theme(axis.title = element_text(size = 6),
        axis.text = element_text(size=5),
        plot.title = element_text(size = 7, face = 'bold',hjust =0),
        axis.line = element_line(size=0.3),
        axis.ticks = element_line(size=0.3),
        text = element_text(family = "sans"),
        legend.text = element_text(size = 6),
        legend.title = element_text(size = 7),
        plot.margin = margin(t = 0, r =0, l=0, b=0))
    P_broadbandbehavinteraction[[p]][[b]] <- q
    
    # print(q)
   
    ## GAM
    # gam_model <- gam(behav ~ ti(power,k=3)+ ti(eeg_age,k=3) + 
    #                    ti(power,eeg_age,k=3)+ sex, data = temp_df_viable,
    #                  na.action = na.exclude)
    # temp_df_clean <- outlier_modelresiduals(temp_df_viable,residuals(gam_model),"lunaid")
    # gamre_model <- gam(behav ~ ti(power,k=3)+ ti(eeg_age,k=3) + 
    #                    ti(power,eeg_age,k=3)+sex+  s(lunaid_clean,bs='re'),
    #                    data = temp_df_clean, na.action = na.exclude)
    # print(summary(gamre_model))

    # predict responses
    # predict_df <- predict_response(gamre_model,terms=c("power[all]","eeg_age"))
    # estimated marginal means
    # emm_gam <- emmeans(gamre_model, ~ power | eeg_age,
    #                       at = list(eeg_age = c(14,20,25),
    #                                 power = seq(min(temp_df_clean$power,na.rm=T),
    #                                             max(temp_df_clean$power, na.rm=T),
    #                                             length.out = 100)))
    # emm_df_gam <- as.data.frame(emm_gam)
    # emm_df_gam$age <- factor(emm_df_gam$eeg_age, levels = c(14,20,25))
    # 
    # q <- ggplot()+
    #   geom_line(data = temp_df_clean, aes(x=power,y=behav,group=lunaid),
    #     alpha = 0.25, size = 0.2,
    #     color=COLOR)+
    #   geom_point(data = temp_df_clean, aes(x=power,y=behav),
    #               color = COLOR,
    #              alpha = 0.25,shape= 16, size = 0.5)+
    #   geom_line(data = emm_df_gam, aes(x=power, y=emmean, color=age),
    #       linewidth=0.5)+
    #   geom_ribbon(data = emm_df_gam,
    #               aes(x=power,fill=age,
    #                   ymin=lower.CL, ymax=upper.CL)
    #               ,color=NA, alpha=0.3)+
    #   scale_color_manual(name="Age (years)",
    #                         values =   lineVALS)+
    #   scale_fill_manual(name="Age (years)",
    #                        values = lineVALS)+
    #   xlab("AS Power (dB)")+
    #   ylab(currbehav_yaxis)+
    #   theme_classic()+
    #  theme(axis.title = element_text(size = 6),
    #     axis.text = element_text(size=5),
    #     plot.title = element_text(size = 7, face = 'bold',hjust =0),
    #     axis.line = element_line(size=0.3),
    #     axis.ticks = element_line(size=0.3),
    #     text = element_text(family = "sans"),
    #     legend.text = element_text(size = 6),
    #     legend.title = element_text(size = 7),
    #     plot.margin = margin(t = 0, r =0, l=0, b=0),
    #     legend.margin = margin(t=0.5, r=0.5,l=0.5,b=0.5))

    # print(q)
  }
  
}

# adjust p-values
R_BroadbandBehavInteraction <- R_BroadbandBehavInteraction %>% 
  mutate(
    p_power_bon = p.adjust(p_interaction,method='bonferroni'),
    p_power_fdr = p.adjust(p_interaction,method='fdr')
  ) 

```

### Glu/GABA asymmetry
#### Main effects
```{r}
# variables to loop over
powertypes <- c("spon","evo")
ei_measures <- c("sipfc.DLPFC_Glu_gamadj",
                 "sipfc.DLPFC_GABA_gamadj",
                 "sipfc.DLPFC_GluGaba_Asym_sqrt")
ei_measures <- c("sipfc.DLPFC_GluGaba_Asym_sqrt")

  # plotting titles
powertypes_titles <- c("Spontaneous","Evoked")

  # Variables being created
R_BroadbandMRSI <- data.frame()
R_BroadbandMRSIBehav <- data.frame()
P_broadbandMRSI <- list()
for (ei in ei_measures){
  for (p in powertypes){
   # color to make plot
  COLOR <- ifelse(
    p=='spon', '#67428F',
    ifelse(
      p =='evo','#388599',
      ifelse(
        p=='tot','black'
        )
      )
    )
    currmetabolite <- metabolite_from_name(ei)
    suffix <- if (currmetabolite=="GluGaba"){
      "_Asym_sqrt"
    } else if (currmetabolite=="Glu" || currmetabolite=="GABA"){
      "_gamadj"
    }
    temp_df_viable <- data.frame(
      lunaid = main_df_viable$lunaid,
      eeg_date = main_df_viable$eeg_date,
      eeg_age = main_df_viable$eeg_age,
      sex = main_df_viable$sex,
      mrsi_age = main_df_viable$sess.age,
      invage = 1/main_df_viable$eeg_age,
      viable = main_df_viable$Viable,
      r_EI = main_df_viable[[paste0("sipfc.R", roi_from_name(ei),"_",currmetabolite,suffix)]],
      l_EI = main_df_viable[[paste0("sipfc.L", roi_from_name(ei),"_",currmetabolite,suffix)]],
      power = main_df_viable[[paste0("corAS_broadband_",p,"power_dB")]],
      behav = main_df_viable$CVLatCor
    )
    # pivot longer and make hemisphere a factor
    temp_df_long <- pivot_longer(temp_df_viable, cols = c("r_EI","l_EI"),
                                 names_to = "hemi",
                                 values_to = "EI")
    temp_df_long$hemi <- as.factor(temp_df_long$hemi)
    # lm model
    lm_model <- lm(power ~ EI + invage + hemi +  sex, 
                   data = temp_df_long, 
                   na.action=na.exclude)
    temp_df_clean <- outlier_modelresiduals(temp_df_long,residuals(lm_model),
                                            "lunaid")
    temp_df_clean$lunaid_clean <- as.factor(temp_df_clean$lunaid_clean)
    # lmer model
    lmer_model <- lmerTest::lmer(power ~ EI + invage + hemi + sex+ (1|lunaid_clean),
                                 data=temp_df_clean,
                                 na.action=na.exclude)
    print(paste(p,ei))
    # print(summary(lmer_model))
    
    
    new_row <- data.frame(powertype= p, ei_measure=ei,
                          p_EI = summary(lmer_model)$coefficients["EI",    
                                                                  "Pr(>|t|)"])
    R_BroadbandMRSI <- rbind(R_BroadbandMRSI,new_row)
    
    # x-axis label for metabolites
    x_label <- if (currmetabolite=="GluGaba"){
      "Glu-GABA asymmetry"
    } else if (currmetabolite == "Glu"){
      "Glutamate"
    } else if (currmetabolite == "GABA"){
      "GABA"
    }
    # simple slopes plot
    # estimated marginal means
    emm_lmer <- emmeans(lmer_model, ~ EI,
                        at = list(EI = seq(min(temp_df_clean$EI,na.rm=T),
                                           max(temp_df_clean$EI,na.rm=T),
                                           length.out=100)))
    emm_df_lmer <- as.data.frame(emm_lmer)

      eipowerfig <- ggplot()+
        geom_line(data=temp_df_clean, 
                  aes(x=EI, y=power,
                      group= interaction(lunaid_clean,hemi)),
                  alpha=0.25,
                  size=0.2,
                  color = COLOR)+
        geom_point(data=temp_df_clean, 
                   aes(x=EI, y=power,
                       shape = hemi),
                   alpha=0.25, 
                   fill = COLOR,
                   color = COLOR,
                   size = 2)+
        scale_shape_manual(name = "Hemisphere",
                           values = c(
                             "r_EI" = 21,
                             "l_EI" = 24
                           ),
                           labels = c(
                             "r_EI" = "R",
                             "l_EI"="L"
                           )) +
        new_scale_color()+
        new_scale_fill()+
        geom_line(data=emm_df_lmer, aes(x=EI, y=emmean),
                    color = COLOR, size = 0.5)+
        geom_ribbon(data=emm_df_lmer, aes(x=EI, ymin=lower.CL, ymax= upper.CL),
                    alpha= 0.3, color=NA,fill = COLOR)+
        xlab(x_label) + 
        ylab("Power (dB)")+
        theme_classic()+
        theme(axis.title = element_text(size = 6),
        axis.text = element_text(size=4.5),
        plot.title = element_text(size = 6, face = 'bold',hjust =0),
        axis.line = element_line(size=0.3),
        axis.ticks = element_line(size=0.3),
        text = element_text(family = "sans"),
        legend.text = element_text(size = 5),
        legend.title = element_text(size =6)
        )
      P_broadbandMRSI[[p]][[ei]] <- eipowerfig
      # print(eipowerfig)
      
      ## GAM
      gam_model <- gam(power ~ s(EI,k=3) + s(eeg_age,k=3) + sex + hemi, data = temp_df_long,
                       na.action = na.exclude)
      temp_df_clean <- outlier_modelresiduals(temp_df_long,residuals(gam_model),"lunaid")
      gamre_model <- gam(power ~ s(EI,k=3) + s(eeg_age,k=3) + sex + hemi+ s(lunaid_clean,bs='re'),
                         data = temp_df_clean, na.action = na.exclude)
      print(summary(gamre_model))
      # simple slopes plot
      # estimated marginal means
    emm_gam <- emmeans(gamre_model, ~ EI,
                        at = list(EI = seq(min(temp_df_clean$EI,na.rm=T),
                                           max(temp_df_clean$EI,na.rm=T),
                                           length.out=100)))
    emm_df_gam <- as.data.frame(emm_gam)

      eipowerfig <- ggplot()+
        geom_line(data=temp_df_clean, 
                  aes(x=EI, y=power,
                      group= interaction(lunaid_clean,hemi)),
                  alpha=0.25,
                  size=0.2,
                  color = COLOR)+
        geom_point(data=temp_df_clean, 
                   aes(x=EI, y=power,
                       shape = hemi),
                   alpha=0.25, 
                   fill = COLOR,
                   color = COLOR,
                   size = 2)+
        scale_shape_manual(name = "Hemisphere",
                           values = c(
                             "r_EI" = 21,
                             "l_EI" = 24
                           ),
                           labels = c(
                             "r_EI" = "R",
                             "l_EI"="L"
                           )) +
        new_scale_color()+
        new_scale_fill()+
        geom_line(data=emm_df_gam, aes(x=EI, y=emmean), color = COLOR, size = 0.5)+
        geom_ribbon(data=emm_df_gam, aes(x=EI, ymin=lower.CL, ymax= upper.CL),
                    alpha= 0.3, color=NA,fill = COLOR)+
        xlab(x_label) + 
        ylab("Power (dB)")+
        theme_classic()+
        theme(axis.title = element_text(size = 6),
        axis.text = element_text(size=4.5),
        plot.title = element_text(size = 6, face = 'bold',hjust =0),
        axis.line = element_line(size=0.3),
        axis.ticks = element_line(size=0.3),
        text = element_text(family = "sans"),
        legend.text = element_text(size = 5),
        legend.title = element_text(size =6)
        )
      print(eipowerfig)

  }
}
  # correcting p-values
R_BroadbandMRSI <- R_BroadbandMRSI %>% group_by(powertype) %>%
  mutate(
    p_EI_bon = p.adjust(p_EI,method="bonferroni"),
    p_EI_fdr = p.adjust(p_EI,method='fdr')
  )


```

#### Interaction effects
```{r}
# variables to loop over
powertypes <- c("spon","evo")
ei_measures <- c("sipfc.DLPFC_Glu_gamadj",
                 "sipfc.DLPFC_GABA_gamadj",
                 "sipfc.DLPFC_GluGaba_Asym_sqrt")
ei_measures <- c("sipfc.DLPFC_GluGaba_Asym_sqrt")

  # plotting titles
powertypes_titles <- c("Spontaneous","Evoked")

  # Variables being created
P_broadbandMRSI_JNplots <- list()
R_BroadbandMRSI_interaction <- data.frame()
R_BroadbandMRSIBehav <- data.frame()
P_broadbandMRSI_interaction <- list()
for (ei in ei_measures){
  for (p in powertypes){
   # color to make plot
  COLOR <- ifelse(
    p=='spon', '#67428F',
    ifelse(
      p =='evo','#388599',
      ifelse(
        p=='tot','black'
        )
      )
    )
    currmetabolite <- metabolite_from_name(ei)
    suffix <- if (currmetabolite=="GluGaba"){
      "_Asym_sqrt"
    } else if (currmetabolite=="Glu" || currmetabolite=="GABA"){
      "_gamadj"
    }
    temp_df_viable <- data.frame(
      lunaid = main_df_viable$lunaid,
      eeg_date = main_df_viable$eeg_date,
      eeg_age = main_df_viable$eeg_age,
      sex = main_df_viable$sex,
      mrsi_age = main_df_viable$sess.age,
      invage = 1/main_df_viable$eeg_age,
      viable = main_df_viable$Viable,
      r_EI = main_df_viable[[paste0("sipfc.R", roi_from_name(ei),"_",currmetabolite,suffix)]],
      l_EI = main_df_viable[[paste0("sipfc.L", roi_from_name(ei),"_",currmetabolite,suffix)]],
      power = main_df_viable[[paste0("corAS_broadband_",p,"power_dB")]],
      behav = main_df_viable$CVLatCor
    )
    # pivot longer and make hemisphere a factor
    temp_df_long <- pivot_longer(temp_df_viable, cols = c("r_EI","l_EI"),
                                 names_to = "hemi",
                                 values_to = "EI")
    temp_df_long$hemi <- as.factor(temp_df_long$hemi)
    # lm model
    lm_model <- lm(power ~ EI * invage + hemi +  sex, 
                   data = temp_df_long, 
                   na.action=na.exclude)
    temp_df_clean <- outlier_modelresiduals(temp_df_long,residuals(lm_model),
                                            "lunaid")
    temp_df_clean$lunaid_clean <- as.factor(temp_df_clean$lunaid_clean)
    # lmer model
    lmer_model <- lmerTest::lmer(power ~ EI * invage + hemi + sex+ (1|lunaid_clean),
                                 data=temp_df_clean,
                                 na.action=na.exclude)
    print(paste(p,ei))
    print(summary(lmer_model))
    
    
    new_row <- data.frame(powertype= p, ei_measure=ei,
                          p_EI = summary(lmer_model)$coefficients["EI",    
                                                                  "Pr(>|t|)"],
                          p_interaction = summary(lmer_model)$coefficients["EI:invage","Pr(>|t|)"])
    R_BroadbandMRSI_interaction <- rbind(R_BroadbandMRSI_interaction,new_row)
    
    if(p=="spon"){
        lineVALS <- c("25" = "#231631",
                                "20" = "#67428F",
                                "14" = "#A585C7")
        pointVALS <-  c("0.04" = "#A585C7",
                                "0.05" = "#67428F",
                                "0.07" = "#231631")
      } else if (p=="evo"){
        lineVALS <-  c("25" = "#132E34",
                                "20" = "#388599",
                                "14" = "#88C4D3")
        pointVALS <- c("0.04" = "#88C4D3",
                                "0.05" = "#388599",
                                "0.07" = "#132E34")
        
      }
    # x-axis label for metabolites
    x_label <- if (currmetabolite=="GluGaba"){
      "Glu-GABA asymmetry"
    } else if (currmetabolite == "Glu"){
      "Glutamate"
    } else if (currmetabolite == "GABA"){
      "GABA"
    }
    # simple slopes plot
    # estimated marginal means
    emm_lmer <- emmeans(lmer_model, ~ EI | invage,
                        at = list(EI = seq(min(temp_df_clean$EI,na.rm=T),
                                           max(temp_df_clean$EI,na.rm=T),
                                           length.out=100),
                                  invage = c(1/14,1/20,1/25)))
    emm_df_lmer <- as.data.frame(emm_lmer)
    emm_df_lmer$age <- factor(1/emm_df_lmer$invage,c(14,20,25))

      eipowerfig <- ggplot()+
        geom_line(data=temp_df_clean, 
                  aes(x=EI, y=power,
                      group= interaction(lunaid_clean,hemi)),
                  alpha=0.25,
                  size=0.2,
                  color = COLOR)+
        geom_point(data=temp_df_clean, 
                   aes(x=EI, y=power,
                       shape = hemi),
                   alpha=0.25, 
                   fill = COLOR,
                   color = COLOR,
                   size = 0.5)+
        scale_shape_manual(name = "Hemisphere",
                           values = c(
                             "r_EI" = 21,
                             "l_EI" = 24
                           ),
                           labels = c(
                             "r_EI" = "R",
                             "l_EI"="L"
                           )) +
        new_scale_color()+
        new_scale_fill()+
        geom_line(data=emm_df_lmer, aes(x=EI, y=emmean,color=age),
                   size = 0.5)+
        geom_ribbon(data=emm_df_lmer, aes(x=EI, ymin=lower.CL, ymax= upper.CL,fill=age),
                    alpha= 0.3, color=NA)+
        scale_color_manual(name = "Age (years)", values = lineVALS) +
      scale_fill_manual(name  = "Age (years)", values = lineVALS) +
        xlab(x_label) + 
        ylab("Power (dB)")+
        theme_classic()+
        theme(axis.title = element_text(size = 6),
        axis.text = element_text(size=4.5),
        plot.title = element_text(size = 6, face = 'bold',hjust =0),
        axis.line = element_line(size=0.3),
        axis.ticks = element_line(size=0.3),
        text = element_text(family = "sans"),
        legend.text = element_text(size = 5),
        legend.title = element_text(size =6)
        )
      P_broadbandMRSI_interaction[[p]][[ei]] <- eipowerfig
      # print(eipowerfig)
      
      # johnson-neyman plot
      recip_trans <- trans_new(
        name = "recip",
        transform = function(x) 1/x,
        inverse = function(x) 1/x
        )
      jn_out <- johnson_neyman(lmer_model, pred = "EI",
                               modx = "invage", sig.color = COLOR,
                               insig.color = 'grey30',
                               line.thickness = 0.5)
      jn_out$plot@layers$geom_segment <- NULL
      jn_plot <- jn_out$plot + theme_classic(base_size = 6)
      jn_plot <- jn_plot + theme(axis.title = element_text(size=6),
                                 axis.text = element_text(size=5),
                                 axis.ticks = element_line(size=0.3),
                                 axis.line = element_line(size=0.3),
                                 legend.title = element_blank()
                                 )+
        scale_x_continuous(name = "Age (years)",
                           trans = recip_trans,
                           labels = c(10,20,30),
                           breaks = c(1/10,1/20,1/30),
                           limits = c(min(temp_df_clean$invage),max(temp_df_clean$invage))
                           )+
        ylab(paste0("Slope of ", x_label, "\non power")) +
        labs(color=NULL,fill=NULL)
      print(jn_plot)
      print(1/jn_out$bounds)
      P_broadbandMRSI_JNplots[[p]][[ei]] <- jn_plot
      
      ## GAM
    #   gam_model <- gam(power ~ ti(EI,k=3) + ti(eeg_age,k=3) + ti(EI,eeg_age,k=3) + sex + hemi, data = temp_df_long,
    #                    na.action = na.exclude)
    #   temp_df_clean <- outlier_modelresiduals(temp_df_long,residuals(gam_model),"lunaid")
    #   gamre_model <- gam(power ~ti(EI,k=3) + ti(eeg_age,k=3) + ti(EI,eeg_age,k=3) + sex
    #                      + hemi+ s(lunaid_clean,bs='re'),
    #                      data = temp_df_clean, na.action = na.exclude)
    #   print(summary(gamre_model))
    #   
    #   # simple slopes plot
    #   # estimated marginal means
    # emm_gam <- emmeans(gamre_model, ~ EI | eeg_age,
    #                     at = list(EI = seq(min(temp_df_clean$EI,na.rm=T),
    #                                        max(temp_df_clean$EI,na.rm=T),
    #                                        length.out=100),
    #                               eeg_age = c(14,20,25)))
    # emm_df_gam <- as.data.frame(emm_gam)
    # emm_df_gam$age <- factor(emm_df_gam$eeg_age,levels = c(14,20,25))
    # 
    #   eipowerfig <- ggplot()+
    #     geom_line(data=temp_df_clean, 
    #               aes(x=EI, y=power,
    #                   group= interaction(lunaid_clean,hemi)),
    #               alpha=0.25,
    #               size=0.2,
    #               color = COLOR)+
    #     geom_point(data=temp_df_clean, 
    #                aes(x=EI, y=power,
    #                    shape = hemi),
    #                alpha=0.25, 
    #                fill = COLOR,
    #                color = COLOR,
    #                size = 2)+
    #     scale_shape_manual(name = "Hemisphere",
    #                        values = c(
    #                          "r_EI" = 21,
    #                          "l_EI" = 24
    #                        ),
    #                        labels = c(
    #                          "r_EI" = "R",
    #                          "l_EI"="L"
    #                        )) +
    #     new_scale_color()+
    #     new_scale_fill()+
    #     geom_line(data=emm_df_gam, aes(x=EI, y=emmean,color=age), size = 0.5)+
    #     geom_ribbon(data=emm_df_gam, aes(x=EI, ymin=lower.CL, ymax= upper.CL,fill=age),
    #                 alpha= 0.3, color=NA)+
    #     scale_color_manual(name = "Age (years)", values = lineVALS) +
    #   scale_fill_manual(name  = "Age (years)", values = lineVALS) +
    #     xlab(x_label) + 
    #     ylab("Power (dB)")+
    #     theme_classic()+
    #     theme(axis.title = element_text(size = 6),
    #     axis.text = element_text(size=4.5),
    #     plot.title = element_text(size = 6, face = 'bold',hjust =0),
    #     axis.line = element_line(size=0.3),
    #     axis.ticks = element_line(size=0.3),
    #     text = element_text(family = "sans"),
    #     legend.text = element_text(size = 5),
    #     legend.title = element_text(size =6)
    #     )
      # print(eipowerfig)

  }
}
  # correcting p-values
R_BroadbandMRSI_interaction <- R_BroadbandMRSI_interaction %>% group_by(powertype) %>%
  mutate(
    p_EI_bon = p.adjust(p_EI,method="bonferroni"),
    p_EI_fdr = p.adjust(p_EI,method='fdr')
  )


```

## ERSP and ITC Clusters
```{r}
# ERSP Clusters with behaviors
run_ersp_behav_analysis <- function(b, df, behavs, behav_labels, plot_clusters = NULL){
  # initialize plot list
  plot_list <- list()
  ## ---- LMER model ----
  # define temp data frame
  temp_df <- data.frame(
    lunaid = df$lunaid,
    eeg_date = df$eeg_date,
    sex = df$sex,
    eeg_age = df$eeg_age,
    invage = df$invage,
    behav = df[[b]],
    visit = df$visitno,
    ASc1 = df$corAS_c1_ersp_interaction,
    ASc2 = df$corAS_c2_ersp_interaction,
    ASc3 = df$corAS_c3_ersp_interaction,
    ASc4 = df$corAS_c4_ersp_interaction,
    ASc5 = df$corAS_c5_ersp_interaction,
    VGSc1 = df$VGS_c1_ersp_interaction,
    VGSc2 = df$VGS_c2_ersp_interaction,
    VGSc3 = df$VGS_c3_ersp_interaction,
    VGSc4 = df$VGS_c4_ersp_interaction,
    VGSc5 = df$VGS_c5_ersp_interaction
    )
  
  lm_model <- lm(behav ~ ASc1 + ASc2 + ASc3 + ASc4 + ASc5 + invage + sex, data = temp_df,
                 na.action = na.exclude)
  df_clean <- outlier_modelresiduals(temp_df, residuals(lm_model), "lunaid")
  lmer_model <- lmerTest::lmer(behav ~ ASc1 + ASc2 + ASc3 + ASc4 + ASc5 + invage + sex + (1|lunaid_clean),
                               data = df_clean,na.action = na.exclude)
  lmer_summary <- summary(lmer_model)
  print(b)
  print(lmer_summary)
  
  ## plot distribution of AS and VGS of cluster ersp and age trajectory if clusters are specified
  if (!is.null(plot_clusters)){
    n_clusts <- length(plot_clusters)
    
    # loop over number of clusters
    for (C in plot_clusters){
      currcluster_df <- clusters_df %>% filter(modelterm == "interaction", 
                                             datatype =="ersp",
                                             clusternum ==C)
      # pivot long    
      df_long <- pivot_longer(df_clean,cols = c(paste0("ASc",C),
                                                paste0("VGSc",C)),
                              names_to = "condition",
                              values_to = "ersp")
      df_long$condition <- as.factor(df_long$condition)
      COLOR <- if (C==1){
        "#C0369D"
        }else if (C==5){
          "#C05936"
        }
      
      VALUES = setNames(c(COLOR, "grey30"), c(paste0("ASc",C), paste0("VGSc",C)))
      LABELS = setNames(c("AS","VGS"), c(paste0("ASc",C), paste0("VGSc",C)))
      
      # view total ERSP developmental trajectory 
      ersptraj_fig <- ggplot(data=df_long, aes(x=eeg_age,
                                                    y=ersp,
                                                    color=condition))+
        # geom_point()+
        geom_smooth(method='lm',
                    formula = y ~ I(1/x), 
                    aes(color = condition,
                        fill=condition),
                    size = 0.5,
                    alpha = 0.1, se=F) +
        scale_fill_manual(values = VALUES,
                          name=NULL,
                          labels = LABELS)+
         scale_color_manual(values =VALUES,
                          name=NULL,
                          labels =  LABELS)+
        xlab("Age (years)")+
        ylab(paste("ERSP (dB)"))+
        theme_classic()+
        theme(
          axis.title = element_text(size=5),
          axis.text = element_text(size=4),
          axis.line = element_line(size=0.3),
          axis.ticks = element_line(size=0.3),
          legend.text = element_text(size=5)
          ) +
        labs(title = paste(round(currcluster_df$minfreq),
                           "-",round(currcluster_df$maxfreq),
                           "Hz cluster",sep=" "))+
        geom_hline(yintercept = 0, linetype = "dashed", color = "black",size = 0.4)
      # print(ersptraj_fig)
      
      # cluster distribution
      ersp_distribution <- ggplot(data=df_long, aes(x=condition,
                                                         y=ersp,
                                                         color=condition))+
        geom_jitter(alpha = 0.75, 
                    size = 0.2,
                    position = position_jitterdodge(jitter.width = 0.25,
                                                    dodge.width = 0.75),
                    shape = 16)+
        stat_slab(aes(fill = condition), 
                  adjust = 0.75,
                  width = 0.6,
                  justification = -0.25,
                  color = NA,
                  alpha = 0.75) +
        geom_boxplot(outlier.shape = NA,
                     width = 0.15, 
                     color='black',
                     fill = NA,
                     size=0.3) + 
        scale_fill_manual(values = VALUES,
                          name=NULL,
                          labels = LABELS)+
        scale_color_manual(values = VALUES,
                           name=NULL,
                           labels =LABELS) + 
        scale_x_discrete(labels = LABELS)+
        ylab(paste("ERSP (dB)"))+
        theme_classic()+
        theme(
          axis.title = element_text(size=5),
          axis.text = element_text(size=4),
          axis.line = element_line(size=0.3),
          axis.ticks = element_line(size=0.3),
          legend.text = element_text(size=5)
          ) +
        labs(title = paste(round(currcluster_df$minfreq),
                           "-",round(currcluster_df$maxfreq),
                           "Hz cluster",sep=" "))
      # print(ersp_distribution)
      
      # behavior vs errp plot
      var_name <- paste0("ASc",C)
      emm <- emmeans(lmer_model, 
               specs = as.formula(paste("~", var_name)),
               at = setNames(
                 list(seq(min(df_clean[[var_name]], na.rm=T),
                          max(df_clean[[var_name]], na.rm=T),
                          length.out = 100)),
                 var_name
               ))
      emm_df <- as.data.frame(emm)
      emm_df <- rename(emm_df, ersp = !!sym(var_name))
      print(colnames(emm_df))
      
      behav_ersp_fig <- ggplot(data = emm_df, aes(x=ersp, y=emmean)) + 
        geom_line(size=0.5,color=COLOR) + 
        geom_ribbon(aes(ymin=lower.CL,ymax=upper.CL),fill = COLOR, alpha = 0.3)+
        theme_classic() + 
        xlab("ERSP (dB)") + ylab(behav_labels[match(b,behavs)])+
        theme(axis.title = element_text(size=5),
              axis.text = element_text(size=4),
              axis.line = element_line(size=0.3),
              axis.ticks = element_line(size=0.3))
      # print(behav_ersp_fig)
      # store in list
      plot_list[[b]][[paste0("cluster", C)]][["ersptraj"]]    <- ersptraj_fig
      plot_list[[b]][[paste0("cluster", C)]][["distribution"]] <- ersp_distribution
      plot_list[[b]][[paste0("cluster", C)]][["behav_ersp"]]  <- behav_ersp_fig
      
      }
  }
  return(list(plot=plot_list))
}

# defining behavior variables
behavs <- c("CorRate","CVLatCor","AvgLatCor")
behav_labels <- c('% correct','Coefficient of variation','Latency (ms)')
results_ersp <- lapply(behavs, run_ersp_behav_analysis,
                  df = main_df_viable,
                  behavs = behavs)
# defining behavior variables
behavs <- c("CorRate","CVLatCor")
results_ersp <- setNames(lapply(behavs, run_ersp_behav_analysis,
                  df = main_df_viable,
                  behavs = behavs,
                  behav_labels = behav_labels,
                  plot_clusters = c(1,5)),behavs)
P_c1_corrate <- results_ersp$CorRate$plot$CorRate$cluster1$behav_ersp
# P_c1_corrate
p_c5_corrate <- results_ersp$CorRate$plot$CorRate$cluster5$behav_ersp
# p_c5_corrate
P_c1_cvlat <- results_ersp$CVLatCor$plot$CVLatCor$cluster1$behav_ersp
# P_c1_cvlat
P_c5_cvlat <- results_ersp$CVLatCor$plot$CVLatCor$cluster5$behav_ersp
# P_c5_cvlat
P_c1_dist <- results_ersp$CVLatCor$plot$CVLatCor$cluster1$distribution
# P_c1_dist
P_c5_dist <- results_ersp$CVLatCor$plot$CVLatCor$cluster5$distribution
# P_c5_dist
P_c1_traj <- results_ersp$CVLatCor$plot$CVLatCor$cluster1$ersptraj
# P_c1_traj 
P_c5_traj <- results_ersp$CVLatCor$plot$CVLatCor$cluster5$ersptraj
# P_c5_traj

## ITC clusters with behaviors
# run_itc_behav_analysis <- function(b, df, behavs,behav_labels,plot_clusters = NULL){
#   # define temp data frame
#   temp_df <- data.frame(
#     lunaid = df$lunaid,
#     eeg_date = df$eeg_date,
#     sex = df$sex,
#     eeg_age = df$eeg_age,
#     invage = df$invage,
#     behav = df[[b]],
#     visit = df$visitno,
#     ASc1 = df$corAS_c1_itc_interaction,
#     ASc2 = df$corAS_c2_itc_interaction,
#     ASc3 = df$corAS_c3_itc_interaction,
#     ASc4 = df$corAS_c4_itc_interaction,
#     ASc5 = df$corAS_c5_itc_interaction,
#     ASc6 = df$corAS_c6_itc_interaction,
#     VGSc1 = df$VGS_c1_itc_interaction,
#     VGSc2 = df$VGS_c2_itc_interaction,
#     VGSc3 = df$VGS_c3_itc_interaction,
#     VGSc4 = df$VGS_c4_itc_interaction,
#     VGSc5 = df$VGS_c5_itc_interaction,
#     VGSc6 = df$VGS_c6_itc_interaction
#   )
#   
#   lm_model <- lm(behav ~ ASc1 + ASc2 + ASc3 + ASc4 + ASc5 + ASc6 + invage + sex, data = temp_df,
#                  na.action = na.exclude)
#   df_clean <- outlier_modelresiduals(temp_df, residuals(lm_model), "lunaid")
#   lmer_model <- lmerTest::lmer(behav ~ ASc1 + ASc2 + ASc3 + ASc4 + ASc5 + ASc6 + invage + sex + (1|lunaid_clean),
#                                data = df_clean,na.action = na.exclude)
#   lmer_summary <- summary(lmer_model)
#   print(b)
#   print(lmer_summary)
#   
#   ## plot distribution of AS and VGS of cluster itc and age trajectory if clusters are specified
#   if (!is.null(plot_clusters)){
#     n_clusts <- length(plot_clusters)
#     
#     # loop over number of clusters
#     for (C in plot_clusters){
#       currcluster_df <- clusters_df %>% filter(modelterm == "interaction", 
#                                              datatype =="itc",
#                                              clusternum ==C)
#       # pivot long    
#       df_long <- pivot_longer(df_clean,cols = c(paste0("ASc",C),
#                                                 paste0("VGSc",C)),
#                               names_to = "condition",
#                               values_to = "itc")
#       df_long$condition <- as.factor(df_long$condition)
#       COLOR <- if (C==1){
#         "#C0369D"
#         }else if (C==5){
#           "#C05936"
#         }
#       COLOR <- 'blue'
#       
#       VALUES = setNames(c(COLOR, "grey30"), c(paste0("ASc",C), paste0("VGSc",C)))
#       LABELS = setNames(c("AS","VGS"), c(paste0("ASc",C), paste0("VGSc",C)))
#       
#       # view total ERSP developmental trajectory 
#       itctraj_fig <- ggplot(data=df_long, aes(x=eeg_age,
#                                                     y=itc,
#                                                     color=condition))+
#         # geom_point()+
#         geom_smooth(method='lm',
#                     formula = y ~ I(1/x), 
#                     aes(color = condition,
#                         fill=condition),
#                     size = 0.5,
#                     alpha = 0.1, se=F) +
#         scale_fill_manual(values = VALUES,
#                           name=NULL,
#                           labels = LABELS)+
#          scale_color_manual(values =VALUES,
#                           name=NULL,
#                           labels =  LABELS)+
#         xlab("Age (years)")+
#         ylab(paste("ITC"))+
#         theme_classic()+
#         theme(
#           axis.title = element_text(size=5),
#           axis.text = element_text(size=4),
#           axis.line = element_line(size=0.3),
#           axis.ticks = element_line(size=0.3),
#           legend.text = element_text(size=5)
#           ) +
#         labs(title = paste(round(currcluster_df$minfreq),
#                            "-",round(currcluster_df$maxfreq),
#                            "Hz cluster",sep=" "))
#         # geom_hline(yintercept = 0, linetype = "dashed", color = "black",size = 0.4)
#       print(itctraj_fig)
#       
#       # cluster distribution
#       itc_distribution <- ggplot(data=df_long, aes(x=condition,
#                                                          y=itc,
#                                                          color=condition))+
#         geom_jitter(alpha = 0.75, 
#                     size = 0.2,
#                     position = position_jitterdodge(jitter.width = 0.25,
#                                                     dodge.width = 0.75),
#                     shape = 16)+
#         stat_slab(aes(fill = condition), 
#                   adjust = 0.75,
#                   width = 0.6,
#                   justification = -0.25,
#                   color = NA,
#                   alpha = 0.75) +
#         geom_boxplot(outlier.shape = NA,
#                      width = 0.15, 
#                      color='black',
#                      fill = NA,
#                      size=0.3) + 
#         scale_fill_manual(values = VALUES,
#                           name=NULL,
#                           labels = LABELS)+
#         scale_color_manual(values = VALUES,
#                            name=NULL,
#                            labels =LABELS) + 
#         scale_x_discrete(labels = LABELS)+
#         ylab(paste("ITC"))+
#         theme_classic()+
#         theme(
#           axis.title = element_text(size=5),
#           axis.text = element_text(size=4),
#           axis.line = element_line(size=0.3),
#           axis.ticks = element_line(size=0.3),
#           legend.text = element_text(size=5)
#           ) +
#         labs(title = paste(round(currcluster_df$minfreq),
#                            "-",round(currcluster_df$maxfreq),
#                            "Hz cluster",sep=" "))
#       print(itc_distribution)
#       
#       # behavior vs errp plot
#       var_name <- paste0("ASc",C)
#       emm <- emmeans(lmer_model, 
#                specs = as.formula(paste("~", var_name)),
#                at = setNames(
#                  list(seq(min(df_clean[[var_name]], na.rm=T),
#                           max(df_clean[[var_name]], na.rm=T),
#                           length.out = 100)),
#                  var_name
#                ))
#       emm_df <- as.data.frame(emm)
#       emm_df <- rename(emm_df, itc = !!sym(var_name))
#       print(colnames(emm_df))
#       
#       behav_itc_fig <- ggplot(data = emm_df, aes(x=itc, y=emmean)) + 
#         geom_line(size=0.5,color=COLOR) + 
#         geom_ribbon(aes(ymin=lower.CL,ymax=upper.CL),fill = COLOR, alpha = 0.3)+
#         theme_classic() + 
#         xlab("ITC") + ylab(behav_labels[match(b,behavs)])+
#         theme(axis.title = element_text(size=5),
#               axis.text = element_text(size=4),
#               axis.line = element_line(size=0.3),
#               axis.ticks = element_line(size=0.3))
#       print(behav_itc_fig)
#       }
#   }
# }
# 
# # defining behavior variables
# behavs <- c("CorRate","CVLatCor","AvgLatCor")
# 
# results_itc <- lapply(behavs, run_itc_behav_analysis,
#                   df = main_df_viable,
#                   behavs = behavs)
# 
# behavs <- c("CVLatCor")
# behav_labels <- c('Coefficient of variation')
# results_itc <- lapply(behavs, run_itc_behav_analysis,
#                   df = main_df_viable,
#                   behavs = behavs,
#                   behav_labels = behav_labels,
#                   plot_clusters = c(3))
```
ERSP interaction clusters:
Correct rate: cluster 1
CV latency: cluster 1 and cluster 5
Average latency: cluster 4

ITC interaction clusters:
Correct rate: cluster 1, cluster 3, cluster 4, cluster 6
CV latency: cluster 3
Average latency: cluster 1, cluster 6

## Spon/evo power and ersp/itc clusters
```{r}
run_power_cluster_analysis <- function(datatype, powertype, cluster, df, sig_color){
  # --- build column names ---
  ersp_col  <- paste0("corAS_c", cluster, "_", datatype, "_interaction")
  power_col <- paste0("corAS_broadband_", 
                      powertype,"power_dB")
  
  # --- outlier removal + lmer ---
  lm_formula  <- as.formula(paste(power_col, "~", ersp_col, "* invage + sex"))
  lm_model    <- lm(lm_formula, data = df, na.action = na.exclude)
  df_clean    <- outlier_modelresiduals(df, residuals(lm_model), "lunaid")
  df_clean$lunaid_clean <- as.factor(df_clean$lunaid_clean)
  
  lmer_formula <- as.formula(paste(power_col, "~", ersp_col, 
                                   "* invage + sex + (1|lunaid_clean)"))
  lmer_model   <- lmerTest::lmer(lmer_formula, data = df_clean, 
                                 na.action = na.exclude)
  print(summary(lmer_model))
  
  # --- emmeans ---
  emm <- emmeans(lmer_model,
                 specs = as.formula(paste("~", ersp_col, "| invage")),
                 at = setNames(
                   list(seq(min(df_clean[[ersp_col]], na.rm=T),
                            max(df_clean[[ersp_col]], na.rm=T),
                            length.out = 100),
                        c(1/14, 1/20, 1/25)),
                   c(ersp_col, "invage")
                   ))
  
  emm_df <- as.data.frame(emm)
  emm_df <- rename(emm_df, ersp = !!sym(ersp_col))
  emm_df$eeg_age <- factor(1/emm_df$invage, levels = c(14, 20, 25))
  
  # --- main interaction plot ---
  if(powertype=="spon"){
        lineVALS <- c("25" = "#231631",
                                "20" = "#67428F",
                                "14" = "#A585C7")
      } else if (powertype=="evo"){
        lineVALS <-  c("25" = "#132E34",
                                "20" = "#388599",
                                "14" = "#88C4D3")
      }

  main_fig <- ggplot() +
    geom_line(data = emm_df,
              aes(x = ersp, y = emmean, color = eeg_age),
              linewidth = 0.5) +
    geom_ribbon(data = emm_df,
                aes(x = ersp, ymin = lower.CL, ymax = upper.CL, fill = eeg_age),
                color = NA, alpha = 0.3) +
    scale_color_manual(name   = "Age (years)",
                       labels = function(x) round(as.numeric(as.character(x)), 0),
                       values = lineVALS) +
    scale_fill_manual(name   = "Age (years)",
                      labels = function(x) round(as.numeric(as.character(x)), 0),
                      values = lineVALS) +
    xlab(paste(toupper(datatype), "(dB)")) +
    ylab(paste(ifelse(powertype == "spon", "Spontaneous", "Evoked"), "power (dB)")) +
    theme_classic() +
    theme(axis.line   = element_line(linewidth = 0.3),
          axis.ticks  = element_line(linewidth = 0.3),
          axis.text   = element_text(size = 5),
          axis.title  = element_text(size = 6),
          legend.text = element_text(size = 5),
          legend.title = element_text(size=6))
  # print(main_fig)
  
   # --- johnson-neyman ---
  recip_trans <- scales::trans_new(
    name      = "recip",
    transform = function(x) 1/x,
    inverse   = function(x) 1/x
    )
  
  jn_out  <- johnson_neyman(lmer_model,
                            pred        = !!sym(ersp_col),
                            modx        = invage,
                            insig.color = "grey30",
                            sig.color   = sig_color,
                            line.thickness = 0.5)
  jn_out$plot@layers$geom_segment <- NULL
  
  jn_fig <- jn_out$plot +
    theme_classic(base_size = 6) +
    theme(axis.title    = element_text(size = 6),
          axis.text     = element_text(size = 5),
          axis.ticks    = element_line(linewidth = 0.3),
          axis.line     = element_line(linewidth = 0.3),
          legend.title  = element_blank()) +
    scale_x_continuous(name   = "Age (years)",
                       trans  = recip_trans,
                       labels = c(10, 20, 30),
                       breaks = c(1/10, 1/20, 1/30),
                       limits = c(min(df_clean$invage), max(df_clean$invage))) +
    ylab(paste("Slope of", toupper(datatype),"on power")) +
    labs(color = NULL, fill = NULL)
  # print(jn_fig)
  
  print(1/jn_out$bounds)
  
  return(list(jn = jn_fig, main = main_fig))
}

# cluster 1, ersp, spontaneous
results_c1ersp_spon <- run_power_cluster_analysis(datatype  = "ersp", 
                           powertype = "spon", 
                           cluster   = 1,
                           df        = main_df_viable,
                           sig_color = "#C0369D")
P_c1ersp_spon_JN <- results_c1ersp_spon$jn
# P_c1ersp_spon_JN
P_c1ersp_spon <- results_c1ersp_spon$main
# P_c1ersp_spon

# cluster 5, ersp, spontaneous
results_c5ersp_spon <- run_power_cluster_analysis(datatype  = "ersp", 
                           powertype = "spon", 
                           cluster   = 5,
                           df        = main_df_viable,
                           sig_color = "#C05936")
P_c5ersp_spon_JN <- results_c5ersp_spon$jn
# P_c5ersp_spon_JN
P_c5ersp_spon <- results_c5ersp_spon$main
# P_c5ersp_spon

# cluster 1, ersp, evoked
results_c1ersp_evo <- run_power_cluster_analysis(datatype  = "ersp", 
                           powertype = "evo", 
                           cluster   = 1,
                           df        = main_df_viable,
                           sig_color = "#C0369D")
P_c1ersp_evo_JN <- results_c1ersp_evo$jn
# P_c1ersp_evo_JN
P_c1ersp_evo <- results_c1ersp_evo$main
# P_c1ersp_evo

# cluster 5, ersp, evoked
results_c5ersp_evo <- run_power_cluster_analysis(datatype  = "ersp", 
                           powertype = "evo", 
                           cluster   = 5,
                           df        = main_df_viable,
                           sig_color = "#C05936")
P_c5ersp_evo_JN <- results_c5ersp_evo$jn
# P_c5ersp_evo_JN
P_c5ersp_evo <- results_c5ersp_evo$main
# P_c5ersp_evo

```

## Paper Figures
### Figure 1: Behavior
```{r}
# LMER plots
P_behav$CorRate + theme(axis.title.x = element_blank(),
                        plot.margin = margin(t=0,
                                                b=0,
                                                r = 1,
                                                l = 0,unit="mm"))+
  P_behav$CVLatCor + theme(plot.margin = margin(t=0,
                                                b=0,
                                                r = 1,
                                                l = 1,unit="mm")) +
  P_behav$AvgLatCor + theme(axis.title.x = element_blank(),
                            plot.margin = margin(t=0,
                                                b=0,
                                                r = 0,
                                                l = 1,unit="mm")) +
        plot_layout(ncol=3)

ggsave("/Volumes/Hera/Abby/AS_EEG/paperfigs/behavior.png", width = 90, height = 45,
       units="mm", dpi = 300 )

# GAM plots
P_behav_gam$CorRate + theme(axis.title.x = element_blank(),
                        plot.margin = margin(t=0,
                                                b=0,
                                                r = 1,
                                                l = 0,unit="mm"))+
  P_behav_gam$CVLatCor + theme(plot.margin = margin(t=0,
                                                b=0,
                                                r = 1,
                                                l = 1,unit="mm")) +
  P_behav_gam$AvgLatCor + theme(axis.title.x = element_blank(),
                            plot.margin = margin(t=0,
                                                b=0,
                                                r = 0,
                                                l = 1,unit="mm")) +
        plot_layout(ncol=3)

ggsave("/Volumes/Hera/Abby/AS_EEG/paperfigs/behavior_gam.png", width = 90, height = 45,
       units="mm", dpi = 300 )
```

### Figure 2: Spontaneous and Evoked age and behavior effects
```{r}
## Difference split significance plots
# Evoked
P_evodiff +  theme(axis.title = element_blank(),
                   plot.margin = margin(0,0,0,0,unit="mm"))

ggsave("/Volumes/Hera/Abby/AS_EEG/paperfigs/evo_diff_sig.png",
       dpi = 400, width = 15, height = 15, units = "mm")
# Spontaneous
P_spondiff +  theme(axis.title = element_blank(),
                   plot.margin = margin(0,0,0,0,unit="mm"))

ggsave("/Volumes/Hera/Abby/AS_EEG/paperfigs/spon_diff_sig.png",
       dpi = 400, width = 15, height = 15, units = "mm")

## Age trajectory and behavior plots
P_spontraj + theme(legend.position = 'none',
                   axis.title.x = element_blank(),
                   plot.margin = margin(0,3,0.5,0,unit="mm")) + 
  ylab("Power (dB)") + 
  P_broadbandbehavinteraction$spon$CorRate + theme(plot.margin = margin(0,2,0.5,3,unit="mm"),
                                                   axis.title.x = element_blank(),
                                                   legend.position = 'none',
                                                   plot.title = element_blank())  +
  P_broadbandbehav$spon$CVLatCor + theme(plot.margin = margin(0,2,0.5,2,unit="mm"),
                                         axis.title.x = element_blank())  +
  P_broadbandbehav$spon$AvgLatCor + theme(plot.margin = margin(0,2,0.5,2,unit="mm"),
                                          axis.title.x = element_blank()) +
  P_evotraj + theme(legend.position = 'none',
                    plot.margin = margin(0.5,3,0,0,unit="mm")) + 
  ylab("Power (dB)") + 
  P_broadbandbehavinteraction$evo$CorRate + theme(plot.margin = margin(0.5,2,0,3,unit="mm"),
                                                  legend.position = 'none',
                                                  plot.title = element_blank())  +
  xlab("AS power (dB)")+
  P_broadbandbehav$evo$CVLatCor + theme(plot.margin = margin(0.5,2,0,2,unit="mm"))  +
  xlab("AS power (dB)")+
  P_broadbandbehav$evo$AvgLatCor + theme(plot.margin = margin(0.5,2,0,2,unit="mm")) +
  xlab("AS power (dB)")+
  plot_layout(nrow = 2, ncol = 4, widths = c(2.5,1,1,1))
ggsave("/Volumes/Hera/Abby/AS_EEG/paperfigs/sponevo_agecondition_behav_corrate_interaction.png", 
       dpi = 400, 
       height = 90, width = 170, units = "mm")

# save interaction legends
spon_corrate_ageinteraction_legend <- get_legend(P_broadbandbehavinteraction$spon$CorRate)
png("/Volumes/Hera/Abby/AS_EEG/paperfigs/spon_corrate_ageinteraction_legend.png",
    width = 15, height = 25, units = "mm", res = 300)
grid.newpage()                       # create a new page
grid.draw(spon_corrate_ageinteraction_legend) # draw the grob
dev.off()   

evo_corrate_ageinteraction_legend <- get_legend(P_broadbandbehavinteraction$evo$CorRate)
png("/Volumes/Hera/Abby/AS_EEG/paperfigs/evo_corrate_ageinteraction_legend.png",
    width = 15, height = 25, units = "mm", res = 300)
grid.newpage()                       # create a new page
grid.draw(evo_corrate_ageinteraction_legend) # draw the grob
dev.off() 

```
#### GAMs
```{r}
## Difference split significance plots
# Evoked
P_evodiff_gam +  theme(axis.title = element_blank(),
                   plot.margin = margin(0,0,0,0,unit="mm"))

ggsave("/Volumes/Hera/Abby/AS_EEG/paperfigs/evo_diff_sig_gam.png",
       dpi = 400, width = 15, height = 15, units = "mm")
# Spontaneous
P_spondiff_gam +  theme(axis.title = element_blank(),
                   plot.margin = margin(0,0,0,0,unit="mm"))

ggsave("/Volumes/Hera/Abby/AS_EEG/paperfigs/spon_diff_sig_gam.png",
       dpi = 400, width = 15, height = 15, units = "mm")

## Age trajectory and behavior plots
P_spontraj_gam + theme(legend.position = 'none',
                   axis.title.x = element_blank(),
                   plot.margin = margin(0,3,0.5,0,unit="mm")) + 
  ylab("Power (dB)") + 
  P_broadbandbehav_gam$spon$CorRate + theme(plot.margin = margin(0,2,0.5,3,unit="mm"),
                                                   axis.title.x = element_blank(),
                                                   legend.position = 'none',
                                                   plot.title = element_blank())  +
  P_broadbandbehav_gam$spon$CVLatCor + theme(plot.margin = margin(0,2,0.5,2,unit="mm"),
                                         axis.title.x = element_blank())  +
  P_broadbandbehav_gam$spon$AvgLatCor + theme(plot.margin = margin(0,2,0.5,2,unit="mm"),
                                          axis.title.x = element_blank()) +
  P_evotraj_gam + theme(legend.position = 'none',
                    plot.margin = margin(0.5,3,0,0,unit="mm")) + 
  ylab("Power (dB)") + 
  P_broadbandbehav_gam$evo$CorRate + theme(plot.margin = margin(0.5,2,0,3,unit="mm"),
                                                  legend.position = 'none',
                                                  plot.title = element_blank())  +
  xlab("AS power (dB)")+
  P_broadbandbehav_gam$evo$CVLatCor + theme(plot.margin = margin(0.5,2,0,2,unit="mm"))  +
  xlab("AS power (dB)")+
  P_broadbandbehav_gam$evo$AvgLatCor + theme(plot.margin = margin(0.5,2,0,2,unit="mm")) +
  xlab("AS power (dB)")+
  plot_layout(nrow = 2, ncol = 4, widths = c(2.5,1,1,1))
ggsave("/Volumes/Hera/Abby/AS_EEG/paperfigs/sponevo_agecondition_behav_corrate_interaction_gam.png", 
       dpi = 400, 
       height = 90, width = 170, units = "mm")
```



### Figure 3: Glu/GABA
```{r}
# just glu/gaba asymmetry
P_broadbandMRSI_interaction$spon$sipfc.DLPFC_GluGaba_Asym_sqrt + 
  theme(legend.position = 'none',
        plot.margin = margin(0,2,0.5,0,unit = "mm"),
        axis.title.x = element_blank()) +
  P_broadbandMRSI_JNplots$spon$sipfc.DLPFC_GluGaba_Asym_sqrt +
  theme(plot.margin = margin(0,0,0.5,2,unit = "mm"),
        axis.title.x = element_blank(),
        legend.position = 'none',
        plot.title = element_blank())+
  P_broadbandMRSI_interaction$evo$sipfc.DLPFC_GluGaba_Asym_sqrt + 
  theme(legend.position = 'none',
        plot.margin = margin(0.5,2,0,0,unit = "mm")) +
  P_broadbandMRSI_JNplots$evo$sipfc.DLPFC_GluGaba_Asym_sqrt + 
  theme(plot.margin = margin(0.5,0,0,2,unit = "mm"),
        plot.title = element_blank(),
        legend.position='none')

ggsave("/Volumes/Hera/Abby/AS_EEG/paperfigs/sponevo_glugaba_jnplot.png",
       dpi = 400, width = 80, height = 80, units = "mm")

# get legends
spon_mrsiinteraction_legend <- get_legend(P_broadbandMRSI_interaction$spon$sipfc.DLPFC_GluGaba_Asym_sqrt)
png("/Volumes/Hera/Abby/AS_EEG/paperfigs/spon_glugabainteraction_legend",
    width = 15, height = 60, units = "mm", res = 600)
grid.newpage()
grid.draw(spon_mrsiinteraction_legend)
dev.off()

evo_mrsiinteraction_legend <- get_legend(P_broadbandMRSI_interaction$evo$sipfc.DLPFC_GluGaba_Asym_sqrt)
png("/Volumes/Hera/Abby/AS_EEG/paperfigs/evo_glugabainteraction_legend",
    width = 15, height = 60, units = "mm", res = 600)
grid.newpage()
grid.draw(evo_mrsiinteraction_legend)
dev.off()

```

### Figure 4: ERSP clusters and behavior
#### load in ERSP data and plot heatmaps
```{r}
## TO DO instead save f-row data in matlab then load that in
# load in matlab data
corAS.ersp_list <- readMat("/Volumes/Hera/Abby/AS_EEG/ERSPdata/corAS_data/prep/corAS_prep_avgtrl_frow_ersp.mat")
corAS.ids_list <- readMat("/Volumes/Hera/Abby/AS_EEG/ERSPdata/corAS_data/prep/corAS_prep_avgtrl_ids.mat")
VGS.ersp_list <- readMat("/Volumes/Hera/Abby/AS_EEG/ERSPdata/VGS_data/prep/VGS_prep_avgtrl_frow_ersp.mat")
VGS.ids_list <- readMat("/Volumes/Hera/Abby/AS_EEG/ERSPdata/VGS_data/prep/VGS_prep_avgtrl_ids.mat")
clusterstats <- readMat("/Volumes/Hera/Abby/AS_EEG/ERSPdata/Cluster_stats/corASvsVGS_ersp_prep_avgtrl.mat")
clustermasks <- readMat("/Volumes/Hera/Abby/AS_EEG/ERSPdata/Cluster_stats/corASvsVGS_tfceresults_ersp_prep_avgtrl.mat")

# unlist variables
times <- as.numeric(corAS.ersp_list[["times"]])
freqs <- as.numeric(corAS.ersp_list[["freqs"]])
corASersp <- corAS.ersp_list[["avg.ersp"]]
VGSersp <- VGS.ersp_list[["avg.ersp"]]
t_age <- clusterstats[["tval"]][[2]]
t_condition <- clusterstats[["tval"]][[3]]
t_interaction <- clusterstats[["tval"]][[4]]
mask_interaction <- clustermasks[["tfce.results"]][[3]][[3]]
mask_age <- clustermasks[["tfce.results"]][[1]][[3]]
mask_condition <- clustermasks[["tfce.results"]][[2]][[3]]
enhancedt_age <- clustermasks[["tfce.results"]][[1]][[1]]
enhancedt_condition <- clustermasks[["tfce.results"]][[2]][[1]]
enhancedt_interaction <- clustermasks[["tfce.results"]][[3]][[1]]

# reshape into dataframe taht can be plotted with ggplot
corAS_df <- melt(corASersp)
colnames(corAS_df) <- c("freq_idx", "time_idx", "value")
corAS_df$time <- times[corAS_df$time_idx]
corAS_df$freq <- freqs[corAS_df$freq_idx]
VGS_df <- melt(VGSersp)
colnames(VGS_df) <- c("freq_idx","time_idx","value")
VGS_df$time <- times[VGS_df$time_idx]
VGS_df$freq <- freqs[VGS_df$freq_idx]

# ERSP heatmaps
# get absolute min and max between corAS and VGS
min_val <- min(c(corAS_df$value, VGS_df$value), na.rm = TRUE)
max_val <- max(c(corAS_df$value, VGS_df$value), na.rm = TRUE)

# AS
corAS_ersp_fig <- ggplot(corAS_df, aes(x = time, y = freq, fill = value)) +
  geom_tile() +
  scale_fill_viridis_c(limits = c(min_val,max_val)) +
  labs(x = "Preparatory time (ms)", y = "Frequency (Hz)", fill = "ERSP (dB)") +
  theme_classic()+
  scale_y_continuous(breaks = c(3,10,20,30,40,50,60,70),
                     expand = c(0,0))+
  scale_x_continuous(breaks = c(0,250,500),
                     expand = c(0,0))+
  ggtitle("Correct AS ERSP") +
  theme(axis.line = element_line(linewidth = 0.3),
        axis.ticks = element_line(size=0.3),
        axis.text = element_text(size=5),
        axis.title = element_text(size=5),
        plot.margin = margin(0,1,1,0,unit="mm"))
# corAS_ersp_fig + theme(legend.position = 'none',
#                        plot.title = element_blank())


# VGS
VGS_ersp_fig <- ggplot(VGS_df, aes(x = time, y = freq, fill = value)) +
  geom_tile() +
  scale_fill_viridis_c(limits = c(min_val,max_val)) +
  labs(x = "Preparatory time (ms)", y = "Frequency (Hz)", fill = "ERSP (dB)") +
  theme_classic()+
  scale_y_continuous(breaks = c(3,10,20,30,40,50,60,70),
                     expand = c(0,0)) +
    scale_x_continuous(breaks = c(0,250,500),
                       expand = c(0,0))+
  ggtitle("VGS ERSP") +
  theme(axis.line = element_line(size=0.3),
        axis.ticks = element_line(size=0.3),
        axis.text = element_text(size=5),
        axis.title = element_text(size=5),
        plot.margin = margin(1,1,0,0,unit="mm"))

# Combine vgs and correct AS
corAS_ersp_fig + theme(legend.position = 'none',
                       plot.title = element_blank(),
                       axis.title.x = element_blank(),
                       axis.text.x = element_blank()) + 
  VGS_ersp_fig + theme(legend.position = 'none',
                       plot.title = element_blank()) + 
  plot_layout(nrow=2)
ggsave("/Volumes/Hera/Abby/AS_EEG/paperfigs/corAS_VGS_ersp.png",
       width = 30, height = 60, units = "mm", dpi = 600)

# save legend
ersp_legend <- get_legend(VGS_ersp_fig)
png("/Volumes/Hera/Abby/AS_EEG/paperfigs/ersp_legend.png",
    width = 20, height = 45, units = 'mm', res = 300)
grid.newpage()
grid.draw(ersp_legend)
dev.off()
```

#### plot clusters
```{r}
# plot t-values and masks from tfce
# interaction
t_interaction_df <- melt(t_interaction)
colnames(t_interaction_df) <- c("freq_idx","time_idx","value")
t_interaction_df$time <- times[t_interaction_df$time_idx]
t_interaction_df$freq <- freqs[t_interaction_df$freq_idx]
mask_interaction_df <- melt(mask_interaction)
colnames(mask_interaction_df) <- c("freq_idx","time_idx","value")
mask_interaction_df$time <- times[mask_interaction_df$time_idx]
mask_interaction_df$freq <- freqs[mask_interaction_df$freq_idx]
mask_interaction_df$value <- as.factor(mask_interaction_df$value)
enhancedt_interaction_df <- melt(enhancedt_interaction)
colnames(enhancedt_interaction_df) <- c("freq_idx","time_idx","value")
enhancedt_interaction_df$time <- times[enhancedt_interaction_df$time_idx]
enhancedt_interaction_df$freq <- freqs[enhancedt_interaction_df$freq_idx]
# age
t_age_df <- melt(t_age)
colnames(t_age_df) <- c("freq_idx","time_idx","value")
t_age_df$time <- times[t_age_df$time_idx]
t_age_df$freq <- freqs[t_age_df$freq_idx]
mask_age_df <- melt(mask_age)
colnames(mask_age_df) <- c("freq_idx","time_idx","value")
mask_age_df$time <- times[mask_age_df$time_idx]
mask_age_df$freq <- freqs[mask_age_df$freq_idx]
mask_age_df$value <- as.factor(mask_age_df$value)
enhancedt_age_df <- melt(enhancedt_age)
colnames(enhancedt_age_df) <- c("freq_idx","time_idx","value")
enhancedt_age_df$time <- times[enhancedt_age_df$time_idx]
enhancedt_age_df$freq <- freqs[enhancedt_age_df$freq_idx]
# condition
t_condition_df <- melt(t_condition)
colnames(t_condition_df) <- c("freq_idx","time_idx","value")
t_condition_df$time <- times[t_condition_df$time_idx]
t_condition_df$freq <- freqs[t_condition_df$freq_idx]
mask_condition_df <- melt(mask_condition)
colnames(mask_condition_df) <- c("freq_idx","time_idx","value")
mask_condition_df$time <- times[mask_condition_df$time_idx]
mask_condition_df$freq <- freqs[mask_condition_df$freq_idx]
mask_condition_df$value <- as.factor(mask_condition_df$value)
enhancedt_condition_df <- melt(enhancedt_condition)
colnames(enhancedt_condition_df) <- c("freq_idx","time_idx","value")
enhancedt_condition_df$time <- times[enhancedt_condition_df$time_idx]
enhancedt_condition_df$freq <- freqs[enhancedt_condition_df$freq_idx]
# round grids to same precision
t_interaction_df$time <- round(t_interaction_df$time, 4)
mask_interaction_df$time <- round(mask_interaction_df$time, 4)
t_interaction_df$freq <- round(t_interaction_df$freq, 4)
mask_interaction_df$freq <- round(mask_interaction_df$freq, 4)

# compute tile sizes
time_res <- min(diff(sort(unique(t_interaction_df$time))))
freq_res <- min(diff(sort(unique(t_interaction_df$freq))))

# contours around clusters
# only contour around cluster 1 and 5
mask_interaction_clust1_5 <- mask_interaction_df %>% mutate(
  value = ifelse(freq >= 44 & freq <= 50.5 &
                   time >=0 & time<=420 & value ==1, 1,
                 ifelse(freq>=44 & freq <48.5 & time>=420 & time <=500 & value ==1,
                        1,
                        ifelse(freq >=29.9 & freq <=32 &
                                 time>=126.5 & time <= 500 & value==1,
                               2,0)))
  )
mask_interaction_clust1_5 <- mask_interaction_clust1_5 %>%
  mutate(
    clust1 = ifelse(value == 1, 1, 0),
    clust2 = ifelse(value == 2, 1, 0)
  )

# just contour around cluster 1
mask_interaction_clust1 <- mask_interaction_df %>%
  mutate(
    value = ifelse(freq >=44 & freq <=50.5 &
                     time >=0 & time <=420 & value ==1, 1,
                   ifelse(freq>=44 & freq <48.5 & time>=420 & time <=500 & value ==1,
                        1,0))
  )
mask_interaction_clust1$value <- as.factor(mask_interaction_clust1$value)
mask_interaction_clust1 <- mask_interaction_clust1 %>%
  mutate(
    clust1 = ifelse(value==1,1,0)
  )

# just contour around cluster 5
mask_interaction_clust5 <- mask_interaction_df %>%
  mutate(
    value = ifelse(freq >=29.9 & freq <=32 &
                                 time>=126.5 & time <= 500 & value==1,
                   1, 0)
  )
mask_interaction_clust5$value <- as.factor(mask_interaction_clust5$value)
mask_interaction_clust5 <- mask_interaction_clust5 %>%
  mutate(
    clust5 = ifelse(value==1,1,0)
  )

# mask of clusters
mask_interaction_fig_clust1_5 <- ggplot() + 
  geom_tile(data=t_interaction_df, aes(x=time,y=freq, fill=value),
            width = time_res, height = freq_res,color=NA) +
  scale_fill_viridis_c(name="t-value",
                       limits = c(-4,4)) +
  guides(fill = 'none')+
  new_scale_fill()+
   geom_contour(data = mask_interaction_clust1_5,
               aes(x=time, y=freq,z = clust1),
               breaks = 1,
               color = "#C0369D",
               linewidth=0.5) +
  geom_contour(data=mask_interaction_clust1_5 ,
               aes(x=time, y=freq,z = clust2),
               breaks = 1,
               color = "#C05936",
               linewidth=0.5)+
  geom_tile(data = mask_interaction_df, aes(x=time,y=freq,fill = value),
            alpha=0.5,
            width = time_res, height = freq_res,color=NA)+
  scale_fill_manual(values = c("1"=NA,
                               "0" = "black"))+
  labs(x = "Preparatory time (ms)", y = "Frequency (Hz)") +
  theme(legend.position = "none")+
  guides(fill="none")+
  theme_classic()+
  scale_y_continuous(breaks = c(3,10,20,30,40,50,60,70),
                     expand = c(0,0)) +
  scale_x_continuous(expand=c(0,0))+
  ggtitle("Interaction Effect") +
  theme(axis.line = element_line(size=0.3),
        axis.ticks = element_line(size=0.3),
        axis.text = element_text(size=5),
        axis.title = element_text(size=6),
        plot.margin = margin(1,1.5,0,0,unit="mm"))

mask_interaction_fig_clust1_5 + theme(plot.title=element_blank())
ggsave("/Volumes/Hera/Abby/AS_EEG/paperfigs/interaction_clusters1_5.png",
       dpi=400, width = 45, height = 95, units = "mm")

# cluster 1
cluster1_mask <- ggplot() + 
  geom_tile(data=t_interaction_df, aes(x=time,y=freq, fill=value),
            width = time_res, height = freq_res,color=NA) +
  scale_fill_viridis_c(name="t-value",
                       limits = c(-4,4)
                       ) +
  guides(fill = 'none')+
  new_scale_fill()+
   geom_contour(data = mask_interaction_clust1,
               aes(x=time, y=freq,z = clust1),
               breaks = 1,
               color = "#C0369D",
               linewidth=0.3) +
  geom_tile(data = mask_interaction_df, aes(x=time,y=freq,fill = value),
            alpha=1,
            width = time_res, height = freq_res,color=NA)+
  scale_fill_manual(values = c("1"=NA,
                               "0" = "black"))+
  geom_tile(data = mask_interaction_clust1, aes(x=time,y=freq,fill = value),
            alpha=0.5,
            width = time_res, height = freq_res,color=NA)+
  scale_fill_manual(values = c("1"=NA,
                               "0" = "black"))+
  labs(x = "Preparatory time (ms)", y = "Frequency (Hz)") +
  theme(legend.position = "none")+
  guides(fill="none")+
  theme_classic()+
  scale_y_continuous(breaks = c(3,10,20,30,40,50,60,70),
                     expand = c(0,0)) +
  scale_x_continuous(expand = c(0,0))+
  ggtitle("Interaction Effect") +
  theme(axis.line = element_line(size=0.3),
        axis.ticks = element_line(size=0.3),
        axis.text = element_text(size=5),
        axis.title = element_text(size=6),
        plot.margin = margin(0,0,0,0,unit="mm"))

cluster1_mask + theme(plot.title = element_blank(),
                      plot.margin = margin(1,1.5,0,0,
                                           unit = "mm")
                      # axis.title = element_blank(),
                      )
ggsave("/Volumes/Hera/Abby/AS_EEG/paperfigs/cluster1_mask.png",
       dpi = 700, height = 43, width = 33, units = "mm")

# cluster 5
cluster5_mask <- ggplot() + 
  geom_tile(data=t_interaction_df, aes(x=time,y=freq, fill=value),
            width = time_res, height = freq_res,color=NA) +
  scale_fill_viridis_c(name="t-value",
                       limits = c(-4,4)
                       ) +
  guides(fill = 'none')+
  new_scale_fill()+
   geom_contour(data = mask_interaction_clust5,
               aes(x=time, y=freq,z = clust5),
               breaks = 1,
               color = "#C05936",
               linewidth=0.3) +
  geom_tile(data = mask_interaction_df, aes(x=time,y=freq,fill = value),
            alpha=1,
            width = time_res, height = freq_res,color=NA)+
  scale_fill_manual(values = c("1"=NA,
                               "0" = "black"))+
  geom_tile(data = mask_interaction_clust5, aes(x=time,y=freq,fill = value),
            alpha=0.5,
            width = time_res, height = freq_res,color=NA)+
  scale_fill_manual(values = c("1"=NA,
                               "0" = "black"))+
  labs(x = "Preparatory time (ms)", y = "Frequency (Hz)") +
  theme(legend.position = "none")+
  guides(fill="none")+
  theme_classic()+
  scale_y_continuous(breaks = c(3,10,20,30,40,50,60,70),
                     expand = c(0,0)) +
  scale_x_continuous(expand = c(0,0))+
  ggtitle("Interaction Effect") +
  theme(axis.line = element_line(size=0.3),
        axis.ticks = element_line(size=0.3),
        axis.text = element_text(size=5),
        axis.title = element_text(size=6),
        plot.margin = margin(0,0,0,0,unit="mm"))

cluster5_mask + theme(plot.title = element_blank(),
                      plot.margin = margin(1,1.5,0,0,
                                           unit = "mm"))
ggsave("/Volumes/Hera/Abby/AS_EEG/paperfigs/cluster5_mask.png",
       dpi = 550, height = 43, width = 33, units = "mm")
```


#### full figure
```{r}
P_c1_dist + theme(plot.title = element_blank(),
                             legend.position = 'none',
                             plot.margin = margin(0,0.5,0,0,unit="mm"),
                             axis.title.x = element_blank())+
 P_c1_traj + theme(plot.title = element_blank(),
                                       legend.position = 'none',
                            plot.margin = margin(0,0.5,0,0.5, unit="mm")) +
  P_c1_corrate +  theme(plot.margin = margin(0,1.5,0,0.5, unit="mm"),
                        plot.title = element_text(size=6))+
  ggtitle("Correct response rate")+
  P_c1_cvlat + theme(plot.margin = margin(0,1.5,0,1.5, unit="mm"),
                     plot.title = element_text(size=6)) +
  ggtitle("Latency variability")+
  plot_layout(nrow =1,ncol=4)

ggsave("/Volumes/Hera/Abby/AS_EEG/paperfigs/c1_traj_behav.png",
       dpi = 400, width = 120, height = 50, units = "mm")

P_c5_dist + theme(plot.title = element_blank(),
                             legend.position = 'none',
                             plot.margin = margin(0,0.5,0,0,unit="mm"),
                             axis.title.x = element_blank())+
 P_c5_traj + theme(plot.title = element_blank(),
                                       legend.position = 'none',
                            plot.margin = margin(0,0.5,0,0.5, unit="mm")) +
  p_c5_corrate +  theme(plot.margin = margin(0,1.5,0,0.5, unit="mm"),
                        plot.title = element_text(size=6))+
  ggtitle("Correct response rate")+
  P_c5_cvlat + theme(plot.margin = margin(0,1.5,0,1.5, unit="mm"),
                     plot.title = element_text(size=6)) +
  ggtitle("Latency variability")+
  plot_layout(nrow =1,ncol=4)

ggsave("/Volumes/Hera/Abby/AS_EEG/paperfigs/c5_traj_behav.png",
       dpi = 400, width = 120, height = 50, units = "mm")

```

### Figure 5: Spon/evo power and ersp clusters
```{r}
# spontaneous
P_c1ersp_spon + theme(legend.position='none',
                    axis.title.x = element_blank(),
                    plot.margin = margin(0,1,2,0, unit= "mm")) +
  P_c1ersp_spon_JN + theme(legend.position = 'none',
                         plot.title = element_blank(),
                         # axis.title.x = element_blank(),
                         plot.margin = margin(0,0,2,1,unit="mm")) +
  P_c5ersp_spon + theme(legend.position='none',
                        axis.title.x = element_blank(),
                        plot.margin = margin(2,1,0,0, unit= "mm")) + 
  P_c5ersp_spon_JN + theme(legend.position = 'none',
                         plot.title = element_blank(),
                         plot.margin = margin(2,0,0,1,unit="mm")) +
  plot_layout(nrow = 2, ncol = 2, widths = c(2,1))
ggsave("/Volumes/Hera/Abby/AS_EEG/paperfigs/spon_clusts.png",
       dpi=400, width = 65, height = 90, units = "mm")


# evoked
P_c1ersp_evo + theme(legend.position='none',
                    axis.title.x = element_blank(),
                    plot.margin = margin(0,1,2,0, unit= "mm")) +
  P_c1ersp_evo_JN + theme(legend.position = 'none',
                         plot.title = element_blank(),
                         # axis.title.x = element_blank(),
                         plot.margin = margin(0,0,2,1,unit="mm")) +
  P_c5ersp_evo + theme(legend.position='none',
                       axis.title.x = element_blank(),
                    plot.margin = margin(2,1,0,0, unit= "mm")) +
  P_c5ersp_evo_JN + theme(legend.position = 'none',
                         plot.title = element_blank(),
                         plot.margin = margin(2,0,0,1,unit="mm")) +
  plot_layout(nrow = 2, ncol = 2, widths = c(2,1))

ggsave("/Volumes/Hera/Abby/AS_EEG/paperfigs/evo_clusts.png",
       dpi=400, width = 65, height = 90, units = "mm")

# get JN legends
clust1_JNlegend <- get_legend(P_c1ersp_spon_JN)
png("/Volumes/Hera/Abby/AS_EEG/paperfigs/clust1_JNlegend.png",
    width = 20, height = 30, units = 'mm', res = 300)
grid.newpage()
grid.draw(clust1_JNlegend)
dev.off()

clust5_JNlegend <- get_legend(P_c5ersp_evo_JN)
png("/Volumes/Hera/Abby/AS_EEG/paperfigs/clust5_JNlegend.png",
    width = 20, height = 30, units = 'mm', res = 300)
grid.newpage()
grid.draw(clust5_JNlegend)
dev.off()
```

## Supplemental figures
### TFCE method
```{r}
## --- t-value maps ---
# interaction
tval_interaction <- ggplot(data = t_interaction_df, aes(x=time,y=freq,fill=value)) +
  geom_tile()+
  scale_fill_viridis_c(name = paste0("t-value"),
                       limits = c(-4,4))+
  xlab("Preparatory time (ms)") +
  ylab("Frequency (Hz)") +
  scale_y_continuous(breaks = c(3,35,70),
                     expand = c(0,0))+
  scale_x_continuous(breaks = c(0,250,500),
                     expand = c(0,0))+
  theme_classic()+
  theme(axis.line = element_line(size=0.2),
        axis.ticks = element_line(size=0.2),
        axis.text = element_text(size=4),
        axis.title = element_text(size=5),
        plot.margin = margin(1,1.5,0,0,unit="mm"))
# age 
tval_age <- ggplot(data = t_age_df, aes(x=time,y=freq,fill=value)) +
  geom_tile()+
  scale_fill_viridis_c(name = paste0("t-value"),
                       limits = c(-4,4))+
  xlab("Preparatory time (ms)") +
  ylab("Frequency (Hz)") +
  scale_y_continuous(breaks = c(3,35,70),
                     expand = c(0,0))+
  scale_x_continuous(breaks = c(0,250,500),
                     expand = c(0,0))+
  theme_classic()+
  theme(axis.line = element_line(size=0.2),
        axis.ticks = element_line(size=0.2),
        axis.text = element_text(size=4),
        axis.title = element_text(size=5),
        plot.margin = margin(1,1.5,0,0,unit="mm"))
# condition
tval_condition <- ggplot(data = t_condition_df, aes(x=time,y=freq,fill=value)) +
  geom_tile()+
  scale_fill_viridis_c(name = paste0("t-value"),
                       limits = c(-4,4))+
  xlab("Preparatory time (ms)") +
  ylab("Frequency (Hz)") +
  scale_y_continuous(breaks = c(3,35,70),
                     expand = c(0,0))+
  scale_x_continuous(breaks = c(0,250,500),
                     expand = c(0,0))+
  theme_classic()+
  theme(axis.line = element_line(size=0.2),
        axis.ticks = element_line(size=0.2),
        axis.text = element_text(size=4),
        axis.title = element_text(size=5),
        plot.margin = margin(1,1.5,0,0,unit="mm"))

## --- Combine and save t value maps ---
tval_age + theme(axis.title = element_blank(),
                 legend.position = 'none',
                 plot.margin = margin(0,1,0,0,unit='mm')) + 
  tval_condition+ theme(axis.title = element_blank(),
                        axis.text.y = element_blank(),
                        legend.position = 'none',
                        plot.margin = margin(0,1,0,1,unit='mm')) + 
  tval_interaction + theme(axis.title = element_blank(),
                           axis.text.y = element_blank(),
                           legend.position = 'none',
                           plot.margin = margin(0,0,0,1,unit='mm'))
ggsave("/Volumes/Hera/Abby/AS_EEG/paperfigs/tval_maps.png",
       width =60,height=20,units='mm', dpi = 600 )
## --- t-value legend ---
tval_legend <- get_legend(tval_age)
png("/Volumes/Hera/Abby/AS_EEG/paperfigs/tval_legend.png",
    width = 15, height = 45, res = 300, units='mm')
grid.newpage()
grid.draw(tval_legend)
dev.off()

## --- enhanced t-value maps ---
# interaction
enhancedtval_interaction <- ggplot(data = enhancedt_interaction_df, aes(x=time,y=freq,fill=value)) +
  geom_tile()+
  scale_fill_viridis_c(name = paste0("Enhanced t-value"),
                       limits = c(0,300))+
  xlab("Preparatory time (ms)") +
  ylab("Frequency (Hz)") +
  scale_y_continuous(breaks = c(3,35,70),
                     expand = c(0,0))+
  scale_x_continuous(breaks = c(0,250,500),
                     expand = c(0,0))+
  theme_classic()+
  theme(axis.line = element_line(size=0.2),
        axis.ticks = element_line(size=0.2),
        axis.text = element_text(size=4),
        axis.title = element_text(size=5),
        plot.margin = margin(1,1.5,0,0,unit="mm"))
# age 
enhancedtval_age <- ggplot(data = enhancedt_age_df, aes(x=time,y=freq,fill=value)) +
  geom_tile()+
  scale_fill_viridis_c(name = paste0("Enhanced t-value"),
                       limits = c(0,300))+
  xlab("Preparatory time (ms)") +
  ylab("Frequency (Hz)") +
  scale_y_continuous(breaks = c(3,35,70),
                     expand = c(0,0))+
  scale_x_continuous(breaks = c(0,250,500),
                     expand = c(0,0))+
  theme_classic()+
  theme(axis.line = element_line(size=0.2),
        axis.ticks = element_line(size=0.2),
        axis.text = element_text(size=4),
        axis.title = element_text(size=5),
        plot.margin = margin(1,1.5,0,0,unit="mm"))
# condition
enhancedtval_condition <- ggplot(data = enhancedt_condition_df, aes(x=time,y=freq,fill=value)) +
  geom_tile()+
  scale_fill_viridis_c(name = paste0("Enhanced t-value"),
                       limits = c(0,300))+
  xlab("Preparatory time (ms)") +
  ylab("Frequency (Hz)") +
  scale_y_continuous(breaks = c(3,35,70),
                     expand = c(0,0))+
  scale_x_continuous(breaks = c(0,250,500),
                     expand = c(0,0))+
  theme_classic()+
  theme(axis.line = element_line(size=0.2),
        axis.ticks = element_line(size=0.2),
        axis.text = element_text(size=4),
        axis.title = element_text(size=5),
        plot.margin = margin(1,1.5,0,0,unit="mm"))

## --- Combine and save enhanced t value maps ---
enhancedtval_age + theme(axis.title = element_blank(),
                 legend.position = 'none',
                 plot.margin = margin(0,1,0,0,unit='mm')) + 
  enhancedtval_condition+ theme(axis.title = element_blank(),
                        axis.text.y = element_blank(),
                        legend.position = 'none',
                        plot.margin = margin(0,1,0,1,unit='mm')) + 
  enhancedtval_interaction + theme(axis.title = element_blank(),
                           axis.text.y = element_blank(),
                           legend.position = 'none',
                           plot.margin = margin(0,0,0,1,unit='mm'))
ggsave("/Volumes/Hera/Abby/AS_EEG/paperfigs/enhancedtval_maps.png",
       width =60,height=20,units='mm', dpi = 600 )
## --- t-value legend ---
enhancedtval_legend <- get_legend(enhancedtval_age)
png("/Volumes/Hera/Abby/AS_EEG/paperfigs/enhancedtval_legend.png",
    width = 35, height = 45, res = 300, units='mm')
grid.newpage()
grid.draw(enhancedtval_legend)
dev.off()

## --- Enhanced t-values with masks ---
mask_enhancedtval_interaction <- ggplot() +
  geom_tile(data = enhancedt_interaction_df, aes(x=time,y=freq,fill=value))+
  scale_fill_viridis_c(name = paste0("Enhanced t-value"),
                       limits = c(0,300))+
  xlab("Preparatory time (ms)") +
  ylab("Frequency (Hz)") +
  scale_y_continuous(breaks = c(3,35,70),
                     expand = c(0,0))+
  scale_x_continuous(breaks = c(0,250,500),
                     expand = c(0,0))+
  new_scale_fill() + 
  geom_tile(data = mask_interaction_df, aes(x=time,y=freq,fill = value),
            alpha=0.5,
            width = time_res, height = freq_res,color=NA)+
  scale_fill_manual(values = c("1"=NA,
                               "0" = "black"))+
  theme_classic()+
  theme(axis.line = element_line(size=0.2),
        axis.ticks = element_line(size=0.2),
        axis.text = element_text(size=4),
        axis.title = element_text(size=5),
        plot.margin = margin(1,1.5,0,0,unit="mm"),
        legend.position = 'none')+
  guides(fill = 'none')

# age 
mask_enhancedtval_age <- ggplot() +
  geom_tile(data = enhancedt_age_df, aes(x=time,y=freq,fill=value))+
  scale_fill_viridis_c(name = paste0("Enhanced t-value"),
                       limits = c(0,300))+
  xlab("Preparatory time (ms)") +
  ylab("Frequency (Hz)") +
  scale_y_continuous(breaks = c(3,35,70),
                     expand = c(0,0))+
  scale_x_continuous(breaks = c(0,250,500),
                     expand = c(0,0))+
  new_scale_fill() + 
  geom_tile(data = mask_age_df, aes(x=time,y=freq,fill = value),
            alpha=0.5,
            width = time_res, height = freq_res,color=NA)+
  scale_fill_manual(values = c("1"=NA,
                               "0" = "black"))+
  theme_classic()+
  theme(axis.line = element_line(size=0.2),
        axis.ticks = element_line(size=0.2),
        axis.text = element_text(size=4),
        axis.title = element_text(size=5),
        plot.margin = margin(1,1.5,0,0,unit="mm"),
        legend.position = 'none')+
  guides(fill = 'none')

# condition
mask_enhancedtval_condition <- ggplot() +
  geom_tile(data = enhancedt_condition_df, aes(x=time,y=freq,fill=value))+
  scale_fill_viridis_c(name = paste0("Enhanced t-value"),
                       limits = c(0,300))+
  xlab("Preparatory time (ms)") +
  ylab("Frequency (Hz)") +
  scale_y_continuous(breaks = c(3,35,70),
                     expand = c(0,0))+
  scale_x_continuous(breaks = c(0,250,500),
                     expand = c(0,0))+
  new_scale_fill() + 
  geom_tile(data = mask_condition_df, aes(x=time,y=freq,fill = value),
            alpha=0.5,
            width = time_res, height = freq_res,color=NA)+
  scale_fill_manual(values = c("1"=NA,
                               "0" = "black"))+
  theme_classic()+
  theme(axis.line = element_line(size=0.2),
        axis.ticks = element_line(size=0.2),
        axis.text = element_text(size=4),
        axis.title = element_text(size=5),
        plot.margin = margin(1,1.5,0,0,unit="mm"),
        legend.position = 'none')+
  guides(fill = 'none')

## --- Combine and save mask enhanced t value maps ---
mask_enhancedtval_age + theme(axis.title = element_blank(),
                 legend.position = 'none',
                 plot.margin = margin(0,1,0,0,unit='mm')) + 
  mask_enhancedtval_condition+ theme(axis.title = element_blank(),
                        axis.text.y = element_blank(),
                        legend.position = 'none',
                        plot.margin = margin(0,1,0,1,unit='mm')) + 
  mask_enhancedtval_interaction + theme(axis.title = element_blank(),
                           axis.text.y = element_blank(),
                           legend.position = 'none',
                           plot.margin = margin(0,0,0,1,unit='mm'))
ggsave("/Volumes/Hera/Abby/AS_EEG/paperfigs/mask_enhancedtval_maps.png",
       width =60,height=20,units='mm', dpi = 600 )

## --- Mask of t-values ---
# interaction
mask_tval_interaction <- ggplot() +
  geom_tile(data = t_interaction_df, aes(x=time,y=freq,fill=value))+
  scale_fill_viridis_c(name = paste0("t-value"),
                       limits = c(-4,4))+
  xlab("Preparatory time (ms)") +
  ylab("Frequency (Hz)") +
  scale_y_continuous(breaks = c(3,35,70),
                     expand = c(0,0))+
  scale_x_continuous(breaks = c(0,250,500),
                     expand = c(0,0))+
  new_scale_fill() + 
  geom_tile(data = mask_interaction_df, aes(x=time,y=freq,fill = value),
            alpha=0.5,
            width = time_res, height = freq_res,color=NA)+
  scale_fill_manual(values = c("1"=NA,
                               "0" = "black"))+
  theme_classic()+
  theme(axis.line = element_line(size=0.2),
        axis.ticks = element_line(size=0.2),
        axis.text = element_text(size=4),
        axis.title = element_text(size=5),
        plot.margin = margin(1,1.5,0,0,unit="mm"),
        legend.position = 'none')+
  guides(fill = 'none')

# age 
mask_tval_age <- ggplot() +
  geom_tile(data = t_age_df, aes(x=time,y=freq,fill=value))+
  scale_fill_viridis_c(name = paste0("t-value"),
                       limits = c(-4,4))+
  xlab("Preparatory time (ms)") +
  ylab("Frequency (Hz)") +
  scale_y_continuous(breaks = c(3,35,70),
                     expand = c(0,0))+
  scale_x_continuous(breaks = c(0,250,500),
                     expand = c(0,0))+
 new_scale_fill() + 
  geom_tile(data = mask_age_df, aes(x=time,y=freq,fill = value),
            alpha=0.5,
            width = time_res, height = freq_res,color=NA)+
  scale_fill_manual(values = c("1"=NA,
                               "0" = "black"))+
  theme_classic()+
  theme(axis.line = element_line(size=0.2),
        axis.ticks = element_line(size=0.2),
        axis.text = element_text(size=4),
        axis.title = element_text(size=5),
        plot.margin = margin(1,1.5,0,0,unit="mm"),
        legend.position = 'none')+
  guides(fill = 'none')
# condition
mask_tval_condition <- ggplot() +
  geom_tile(data = t_condition_df, aes(x=time,y=freq,fill=value))+
  scale_fill_viridis_c(name = paste0("t-value"),
                       limits = c(-4,4))+
  xlab("Preparatory time (ms)") +
  ylab("Frequency (Hz)") +
  scale_y_continuous(breaks = c(3,35,70),
                     expand = c(0,0))+
  scale_x_continuous(breaks = c(0,250,500),
                     expand = c(0,0))+
 new_scale_fill() + 
  geom_tile(data = mask_condition_df, aes(x=time,y=freq,fill = value),
            alpha=0.5,
            width = time_res, height = freq_res,color=NA)+
  scale_fill_manual(values = c("1"=NA,
                               "0" = "black"))+
  theme_classic()+
  theme(axis.line = element_line(size=0.2),
        axis.ticks = element_line(size=0.2),
        axis.text = element_text(size=4),
        axis.title = element_text(size=5),
        plot.margin = margin(1,1.5,0,0,unit="mm"),
        legend.position = 'none')+
  guides(fill = 'none')

## --- Combine and save t value maps ---
mask_tval_age + theme(axis.title = element_blank(),
                 legend.position = 'none',
                 plot.margin = margin(0,1,0,0,unit='mm')) + 
  mask_tval_condition+ theme(axis.title = element_blank(),
                        axis.text.y = element_blank(),
                        legend.position = 'none',
                        plot.margin = margin(0,1,0,1,unit='mm')) + 
  mask_tval_interaction + theme(axis.title = element_blank(),
                           axis.text.y = element_blank(),
                           legend.position = 'none',
                           plot.margin = margin(0,0,0,1,unit='mm'))
ggsave("/Volumes/Hera/Abby/AS_EEG/paperfigs/mask_tval_maps.png",
       width =60,height=20,units='mm', dpi = 600 )
```

### Sex differences
```{r}

```



